### 2014-10-16 RotacionOutFlows/Paper/ms.tex
paper

\documentclass{emulateapj}
\usepackage{multirow,color,wrapfig,ulem}
\usepackage {graphicx}
\usepackage{graphics}
\usepackage[dvips]{epsfig}
\newcommand{\kms}{{\ifmmode{{\mathrm{\,km\ s}^{-1}}}\else{\,km~s$^{-1}$}\fi}}
\newcommand{\lya}{{Ly-$\alpha$~}}
\begin{document}

\title{Titulo} 
\shorttitle{shorttitle}

\shortauthors{Remolina-Gutierrez, Forero-Romero \&Garavito-Camargo}

\author{ Maria Camila Remolina-Gutierrez, Jaime E. Forero-Romero, Juan N. Garavito-Camargo}
\affil{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia}
\email{mc.remolina197@uniandes.edu.co}
\email{je.forero@uniandes.edu.co}
\email{jn.garavito57@uniandes.edu.co}

\keywords{Lyman Alpha Emission,  } 
\begin{abstract}
Here goes the abstract....
\end{abstract}

\section{Introduction}
\label{sec:intro}

The Lyman-Alpha emission line is the spectral line produced when an electron goes from the second energy level to the first, loosing energy and emmiting it as light. When this energy decays are seen in Hydrogen atoms, the wavelenght of the \lya line is 121.567 nm. The detection of this emission line is a main tecnique in extragalactic astronomy because galaxies with a strong emission of this (called Lyman Alpha Emitters - LAEs) are used to study the evolution of the universe in big scale. \\

LAEs are young and far away galaxies with most of its matter composed by Hydrogen atoms, being the rest heavier elements, like Iron, produced by growing stars burning their material. Then, this spectral line tells very important information about the galaxy, most of it actually, which creates a motivation to find a way to model the \lya line according to certain free parameters that vary from a galaxy to another and that can be obtained from observations. \\

Our purpose in this paper is then to make a theoretical model, based on radiative transfer simulations, that use MonteCarlo computational methods to emulate how the line profile is going to come out of the galaxy if it is rotating and has a surrounding outflow, both of this phenomena characterized by key parameters that are going to be described further on the paper. \\

---------------------------------------------------------------------\\
MISSING: What has been done related to this? (In the astronomy world)\\
-----------------------------------------------------------------------\\

---------------------------------------------------------------------\\
MISSING: Intro to rotation model (and its analytic aproximation)\\
-----------------------------------------------------------------------\\

---------------------------------------------------------------------\\
MISSING: Intro to the ThinShell outflow model\\
-----------------------------------------------------------------------\\

\section{Theoretical Frame}
In this section we are going to describes the two different models that are used in this project, that are able to reproduce a real and consistent line.\\

---------------------------------------------------------------------\\
MISSING: \\
- Express prettier the intro of the section\\
-----------------------------------------------------------------------\\

\subsection{Rotation Model}

---------------------------------------------------------------------\\
MISSING: \\
- Full explanation.\\
- Ref: Jaime And Juan Nicolas\\
-----------------------------------------------------------------------\\

\subsection{Outflow Model: ThinShell}

---------------------------------------------------------------------\\
MISSING:\\
- Important equations and description of the parameters\\
- Why we use ThinShel instead of Wind. Its advantages (explains redshift, avoids re-difussion, bounces).\\
- Ref: Alvaro and Julian
-----------------------------------------------------------------------\\

\subsection{Joint Model}

---------------------------------------------------------------------\\
MISSING: \\
- Full explanation.\\
- How exactly are this 2 mixed\\
- Tell and make a detailed explanation of the free parameters that we are going to explore. \\
-----------------------------------------------------------------------\\

\section{Results}
\label{sec:results}
Here goes the results....

---------------------------------------------------------------------\\
MISSING: \\
- What are the compact results.\\
- Some plots.\\
- Not a physical analysis yet. \\
-----------------------------------------------------------------------\\

\section{Discussion}
\label{sec:discussion}

---------------------------------------------------------------------\\
MISSING: \\
- Comparison with some other result (probably observations).\\
- Why is this result useful? \\
- What possible implications can this model have?\\
-----------------------------------------------------------------------\\

\section{Conclusions}
\label{sec:conclusions}
Here goes the conclusions....

\section*{Acknowledgments}

To

The data, source code and instructions to
replicate the results of this paper can be found
here {\texttt{https://github.com/mariacamilaremolinagutierrez/ LymanAlpha/}}.
Most of our code benefits from the work of the IPython and Matplotlib
communities \citep{IPython,matplotlib}.

---------------------------------------------------------------------\\
MISSING: \\
- Help from Alvaro and Julian: data, explanations, advice and collaboration. \\
- Soooo many more acknowledgments.\\
-----------------------------------------------------------------------\\

---------------------------------------------------------------------\\
MISSING IN REFERENCES: \\
- A loooot of references not here yet.\\
- Alvaro's paper.(Can galactic outflows explain the properties of Lyα emitters?
Alvaro Orsi, Cedric G. Lacey and Carlton M. Baugh)\\
- Use the correct citation method. \\
-----------------------------------------------------------------------\\

\bibliographystyle{apj}
\begin{thebibliography}{38}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

\bibitem[{{Forero-Romero} {et~al.}(2011){Forero-Romero}, {Yepes},
  {Gottl{\"o}ber}, {Knollmann}, {Cuesta}, \& {Prada}}]{CLARA}
{Forero-Romero}, J.~E., {Yepes}, G., {Gottl{\"o}ber}, S., {Knollmann}, S.~R.,
  {Cuesta}, A.~J., \& {Prada}, F. 2011, \mnras, 415, 3666

\bibitem[{{Verhamme} {et~al.}(2006){Verhamme}, {Schaerer}, \&
  {Maselli}}]{Verhamme06}
{Verhamme}, A., {Schaerer}, D., \& {Maselli}, A. 2006, \aap, 460, 397

\bibitem[{P\'erez \& Granger(2007)}]{IPython}
P\'erez, F., \& Granger, B.~E. 2007, Computing in Science and Engineering, 9, 21

\end{thebibliography}

\newpage

%\section{Ejemplos para tener en cuenta}
%\label{sec:implementation}
%
%Ejemplo de ecuacion
%  
%\begin{equation}
%    v_{x}=-\frac{y}{R}V_{\rm max}, \label{subeq1}
%\end{equation}
%
%Ejemplo referencia a figura
%
%In Fig. \ref{fig:geometry} se ve .....
%
%Ejemplo cita 
%
%Scape of  at line center, which has also been associated with escape of ionizing (LyC) photons
%\citep{Behrens2014,2014arXiv1404.2958V}
% 
%Ejemplo display math
%
%\begin{displaymath}
%J(x,b,\phi,i)=\frac{\sqrt{\pi}}{\sqrt{24}a\tau_0}\Bigg{(}\frac{(x-x_{\rm
%    b})^2}{1+{\rm cosh}\Big{[}\sqrt{\frac{2\pi^3}{27}}\frac{|(x
%      -x_{\rm b})^3|}{a\tau_0}\Big{]}}\Bigg{)},
%\end{displaymath} 
%
%Ejemplo de figura
%
%\begin{figure}
%\begin{center}
%  \includegraphics[width=0.4\textwidth]{ejemplofigura}
%\end{center}
%\caption{Ejemplo caption figura.  
%    \label{fig:geometry}}  
%\end{figure}
%
%Ejemplo tabla
%
%\begin{table}
%\begin{center}
%\begin{tabular}{c cccccc}
%\hline \hline
%Source & $\tau_{H}$ & &  $\ V_{\rm max}$& & \\
%Distribution& &    & (\kms) & & \\ 
%& & 0 & 100 &200 & 300\\ \hline 
%Homogeneous & $10^{5}$& 0.263 &  0.263 &  0.263 &  0.263  \\
%            & $10^{6}$ & 0.291 &   0.292 &  0.293 &  0.293 \\
%Central & $10^{5}$ &  0.096 & 0.096 &  0.096 & 0.096 \\
%  		&$10^{6}$ & 0.066 &  0.066 &  0.066 &  0.066 \\
%\hline
%\end{tabular}
%\caption{
% Ejemplo de tabla. } 
%\label{table:escape}
%\end{center}
%\end{table}

\end{document}

### 2014-10-27 RotacionOutFlows/Paper/ms.tex
continue intro

@@
 
----------------------------------------------------------------------\\
-MISSING: Intro to rotation model (and its analytic aproximation)\\
------------------------------------------------------------------------\\
+As it has been described, the main purpose of this project is to mix a rotating galaxy with an external outflow surrounding it and analyze the resulting spectrum.
+The rotation model for the LAE consists on a sphere with an homogeneous mixture of dust and hydrogen at a constant temperature undergoing a solid-body rotation.
+The spectrum then depends on the maximum velocity of the sphere, the neutral hydrogen optical depths and the viewing angle.
+What happens is that photons are emmited from the an homogeneus distribution of gas and escape the sphere after a radiative transfer process that ends at the border.\\
 
----------------------------------------------------------------------\\
-MISSING: Intro to the ThinShell outflow model\\
------------------------------------------------------------------------\\
+In this model, rotation does not induce any spatial anisotropy in the integrated line flux, the escape fraction or the average number of scatterings, which led to the creation of an analytic approximation for the galaxy spectrum.
+This mathematical expression helps to minimize the computational costs and lets try with several parameters without spending great amounts of time running the code.
+\\
+
+After this photons escape the galaxy to empty space, they encounter a thin spherical shell of matter at a certain radius from the center.
+That material is the outflow of the LAE, created mainly by starbursts which composition is characterized with the parameters of Hydrogen column density and metallicity.
+Besides its components, the galactic outflow is also defined by an expanding constant velocity that affects the redshift of the photons.\\
+
+As there is a lot of empty space inside the shell, it acts as a reflector of photons.
+This means, that when one wants to comes out it is most likely to bounce inside the sphere several times before finally escaping.
+However it is not likely that the photon comes back again inside the galaxy, which helps that the first process does not have to be repeated, and both stages can be treated as consecutive, not simultaneous.
+\\
 
 \section{Theoretical Frame}
-In this section we are going to describes the two different models that are used in this project, that are able to reproduce a real and consistent line.\\
+In this section we are going to describe the two different models that are used in this project, that are able to reproduce a real and consistent line.\\
 

### 2014-10-27 RotacionOutFlows/Paper/ms.tex
little change

@@
 ---------------------------------------------------------------------\\
-MISSING: What has been done related to this? (In the astronomy world)\\
+MISSING: What has been done related to this?\\
 -----------------------------------------------------------------------\\
@@
 The spectrum then depends on the maximum velocity of the sphere, the neutral hydrogen optical depths and the viewing angle.
-What happens is that photons are emmited from the an homogeneus distribution of gas and escape the sphere after a radiative transfer process that ends at the border.\\
+What happens is that photons are emmited from a central distribution of gas and escape the sphere after a radiative transfer process that ends at the border.\\
 

### 2014-10-29 RotacionOutFlows/Paper/ms.tex
more paper

@@
 \newcommand{\lya}{{Ly-$\alpha$~}}
+\newcommand{\ang}{{$\theta_{gal}$~}}
+\newcommand{\lognh}{{$\log{nH}$~}}
+\newcommand{\vel}{{$v_{out}$~}}
+
 \begin{document}
@@
 \section{Theoretical Frame}
+\label{sec:theo}
 In this section we are going to describe the two different models that are used in this project, that are able to reproduce a real and consistent line.\\
@@
 \subsection{Rotation Model}
-
 ---------------------------------------------------------------------\\
@@
 - Why we use ThinShel instead of Wind. Its advantages (explains redshift, avoids re-difussion, bounces).\\
-- Ref: Alvaro and Julian
+- Ref: Alvaro and Julian\\
 -----------------------------------------------------------------------\\
@@
 - Tell and make a detailed explanation of the free parameters that we are going to explore. \\
+- State the fixed parameters.\\
 -----------------------------------------------------------------------\\
@@
 - Not a physical analysis yet. \\
+- Write 
 -----------------------------------------------------------------------\\
+
+\subsection{Influences of the Free Parameters}
+
+In order to study the influence of each of the three free parameters, we fix two of them and see how the final spectrum varies along the other one left. In each case we will state these changes.
+
+\subsubsection{Influence of the Galaxy Viewing Angle: \ang}
+
+If one sets fixed outflow \vel and \lognh in each case the viewing angle has the same effect: it increases proportionally the intensity.
+However this change is not that significant.
+The resulting spectrums are completely the same, but enlarged vertically by a small factor, being $90^\circ$ the most intense one and $0^\circ$ the opposite.\\
+
+\subsubsection{Influence of the Hydrogen Column Density: \lognh }
+
+The effect of the \lognh is the creation of 2 peaks: the left one very thin, tall and pronounced, and the right one very wide, small and soften.
+When the $log{nH}$ is increased, the left peak starts to decrease while mixing with the right one, decreasing ther height ratio until the left peak completely dissapears.
+The resulting spectrum, with high column density, is a wide single mountain with intensity significantly less than at the beginning.
+Fig.
+\ref{fig:influence_lognH} helps visualize this effect in a better way.\\
+
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.4\textwidth]{./figures/influence_lognH.png}
+\end{center}
+\caption{\textbf{Influence of Hydrogen Column Density:} The values of the fixed parameters are \vel = 100 \kms and \ang = 90$^\circ$.
+There are three stages of the \lognh value shown: initial, intermediate and final, with the values shown on the plot.
+\label{fig:influence_lognH}}  
+\end{figure}
 
@@
 -----------------------------------------------------------------------\\
+
+Ideas: \\
+
+The decrease of the intensity while increasing the column density is caused because the column density is proportional to the absortion of light in the gas.
+The more $log{nH}$, the less photons get out of the outflow.
 
@@
 %
-%Ejemplo de figura
-%
-%\begin{figure}
-%\begin{center}
-%  \includegraphics[width=0.4\textwidth]{ejemplofigura}
-%\end{center}
-%\caption{Ejemplo caption figura.  
-%    \label{fig:geometry}}  
-%\end{figure}
-%
 %Ejemplo tabla

### 2014-10-29 RotacionOutFlows/Paper/ms.tex
more paper

@@
 \label{sec:theo}
-In this section we are going to describe the two different models that are used in this project, that are able to reproduce a real and consistent line.\\
+In this section we are going to describe the two different models that are used in this project, that are able to reproduce a real and consistent \lya profile.\\
 
@@
 - Not a physical analysis yet. \\
-- Write 
+- Write better (prettier)\\
 -----------------------------------------------------------------------\\
@@
 The resulting spectrums are completely the same, but enlarged vertically by a small factor, being $90^\circ$ the most intense one and $0^\circ$ the opposite.\\
+
+---------------------------------------------------------------------\\
+MISSING: \\
+- Figure that explains better.\\
+-----------------------------------------------------------------------\\
 
@@
 \end{figure}
+
+\subsubsection{Influence of the Outflow Expanding Velocity: \vel }
+
+---------------------------------------------------------------------\\
+MISSING: \\
+- Influence Outflow Velocity.\\
+-----------------------------------------------------------------------\\
 

### 2014-10-29 RotacionOutFlows/Paper/ms.tex
more paper

@@
 However this change is not that significant.
-The resulting spectrums are completely the same, but enlarged vertically by a small factor, being $90^\circ$ the most intense one and $0^\circ$ the opposite.\\
+The resulting spectrums are completely the same, but enlarged vertically by a small factor.
+Fig.
+\ref{fig:influence_ang} helps visualize this effect in a better way.\\
 
----------------------------------------------------------------------\\
-MISSING: \\
-- Figure that explains better.\\
------------------------------------------------------------------------\\
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.4\textwidth]{./figures/influence_ang.png}
+\end{center}
+\caption{\textbf{Influence of Galaxy Viewing Angle:} The values of the fixed parameters are \vel = 100 \kms and \lognh = 21.3125.
+The 3 possible angles are shown in the plot with different colors.
+The increase is visible as well as its small enlargement factor.\\
+\label{fig:influence_ang}}  
+\end{figure}
 
@@
 \caption{\textbf{Influence of Hydrogen Column Density:} The values of the fixed parameters are \vel = 100 \kms and \ang = 90$^\circ$.
-There are three stages of the \lognh value shown: initial, intermediate and final, with the values shown on the plot.
+There are three stages of the \lognh value shown: initial, intermediate and final, with the values shown on the plot.\\
 \label{fig:influence_lognH}}  
@@
 
-To
+To ...\\
 
@@
 Most of our code benefits from the work of the IPython and Matplotlib
-communities \citep{IPython,matplotlib}.
+communities \citep{IPython,matplotlib}.\\
 

### 2014-11-13 RotacionOutFlows/Paper/ms.tex
more things

@@
-\documentclass{emulateapj}
-\usepackage{multirow,color,wrapfig,ulem}
-\usepackage {graphicx}
-\usepackage{graphics}
-\usepackage[dvips]{epsfig}
-\newcommand{\kms}{{\ifmmode{{\mathrm{\,km\ s}^{-1}}}\else{\,km~s$^{-1}$}\fi}}
-\newcommand{\lya}{{Ly-$\alpha$~}}
-\newcommand{\ang}{{$\theta_{gal}$~}}
-\newcommand{\lognh}{{$\log{nH}$~}}
-\newcommand{\vel}{{$v_{out}$~}}
+%Document Class
+\documentclass{latex/emulateapj}
+
+%Packages and Commands
+\include{latex/packages_commands}
 
@@
 
-\keywords{Lyman Alpha Emission,  } 
+\keywords{Lyman Alpha Emission,  ....MISSING....}
+
 \begin{abstract}
-Here goes the abstract....
+\noindent ------------------------------------------------------------------------------------------------------------------------------------\\
+MISSING: The abstract\\
+------------------------------------------------------------------------------------------------------------------------------------\\
 \end{abstract}
@@
 
-\section{Theoretical Frame}
+\section{Theoretical Background}
 \label{sec:theo}
@@
 The effect of the \lognh is the creation of 2 peaks: the left one very thin, tall and pronounced, and the right one very wide, small and soften.
-When the $log{nH}$ is increased, the left peak starts to decrease while mixing with the right one, decreasing ther height ratio until the left peak completely dissapears.
+When the $log{nH}$ is increased, the left peak starts to decrease while mixing with the right one, decreasing their height ratio until the left peak completely dissapears.
 The resulting spectrum, with high column density, is a wide single mountain with intensity significantly less than at the beginning.
@@
 
-\bibliographystyle{apj}
-\begin{thebibliography}{38}
-\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
-
-\bibitem[{{Forero-Romero} {et~al.}(2011){Forero-Romero}, {Yepes},
-  {Gottl{\"o}ber}, {Knollmann}, {Cuesta}, \& {Prada}}]{CLARA}
-{Forero-Romero}, J.~E., {Yepes}, G., {Gottl{\"o}ber}, S., {Knollmann}, S.~R.,
-  {Cuesta}, A.~J., \& {Prada}, F. 2011, \mnras, 415, 3666
-
-\bibitem[{{Verhamme} {et~al.}(2006){Verhamme}, {Schaerer}, \&
-  {Maselli}}]{Verhamme06}
-{Verhamme}, A., {Schaerer}, D., \& {Maselli}, A. 2006, \aap, 460, 397
-
-\bibitem[{P\'erez \& Granger(2007)}]{IPython}
-P\'erez, F., \& Granger, B.~E. 2007, Computing in Science and Engineering, 9, 21
-
-\end{thebibliography}
+\bibliographystyle{latex/mn2e}
+\bibliography{references}
 
@@
 %In Fig. \ref{fig:geometry} se ve .....
-%
-%Ejemplo cita 
-%
-%Scape of  at line center, which has also been associated with escape of ionizing (LyC) photons
-%\citep{Behrens2014,2014arXiv1404.2958V}
 % 

### 2014-11-15 RotacionOutFlows/Paper/ms.tex
larger images correct
Rotation Model

@@
 \documentclass{latex/emulateapj}
+\usepackage{multirow,color,wrapfig,ulem}
 
@@
 \include{latex/packages_commands}
+\usepackage{multirow,color,wrapfig,ulem}
+\usepackage{graphicx}
+\usepackage{graphics}
+\usepackage[dvips]{epsfig}
+\newcommand{\avg}[1]{\langle{#1}\rangle}
+\newcommand{\nscatt}{\langle N_{\rm  scatt}\rangle}
+\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha~}\else{Ly$\alpha$~}\fi}}
+\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}
+\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc }\fi}}
+\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}
+\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}
+\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm{M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}
+\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm{M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}
+\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}
+\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}
+%\newcommand{\lya}{{Lyman $\alpha$~}}
+\newcommand{\clara}{{\texttt{CLARA}}~}
+\newcommand{\rand}{{\ifmmode{{\mathcal{R}}}\else{${\mathcal{R}}$ }\fi}}
+\newcommand{\hs}{{\hspace{1mm}}}
+%\newcommand{\kms}{{\ifmmode{{\mathrm{\,km\ s}^{-1}}}\else{\,km~s$^{-1}$}\fi}}
 
@@
 \label{sec:theo}
-In this section we are going to describe the two different models that are used in this project, that are able to reproduce a real and consistent \lya profile.\\
+In this section we describe the two different models that are used in this project,
+that are able to reproduce a real and consistent \lya profile. As first we implement
+the rotation followed by an outflow.\\
 
@@
 \subsection{Rotation Model}
----------------------------------------------------------------------\\
-MISSING: \\
-- Full explanation.\\
-- Ref: Jaime And Juan Nicolas\\
------------------------------------------------------------------------\\
+
+We use the simplified rotation model developed by [garavito-camargo et al]
+in which a rotating galaxy is modeled as a solid rotating sphere, with a homogeneous mixture
+of hydrogen and dust. Photons can be initially at the center or can be
+homogeneously distributed inside the sphere. The equations governing this
+ solid-body rotation sphere in which the axys of rotation is defined to be allign
+ with the $z$-axys are:
+
+\begin{equation}
+    v_{x}=-\frac{y}{R}V_{\rm max}, \label{subeq1}
+\end{equation}
+\begin{equation}
+    v_{y}=\frac{x}{R}V_{\rm max}, \label{subeq2}
+\end{equation}
+\begin{equation}
+    v_{z}=0, \label{subeq3}
+\end{equation}
+%
+
+Where $R$ is the radius of the sphere and $V_{\rm max}$ is the linear
+velocity at the sphere's surface. The minus/plus sign in the
+$x$/$y$-component of the velocity indicates the direction of
+rotation. In this case we take the angular velocity in the same
+direction as the $\hat{k}$ unit vector.
+
+In this work we use the analytical expression for rotation derived in [garavito-camargo et al]
+where a rotating sphere can be seen as a static sphere in the laboratory
+frame with a bulk velocity difference in each surface element with respect
+to a distant observer. With the previous analysis the outcoming spectra can be
+expressed as:
+
+\begin{equation}
+J(x,i) \approx 2\pi \int_0^Rdb \hs b
+\int_0^{2\pi}d\phi \hs J(x,b,\phi,i),
+\end{equation}
+
+Where $J(x, b, \phi, i)$ is the spectrum of the flux emerging from the
+surface at point $(b, \phi)$ and is expressed as:
+
+\begin{equation}
+J(x,b,\phi,i)=\frac{\sqrt{\pi}}{\sqrt{24}a\tau_0}\Bigg{(}\frac{(x-x_{\rm
+    b})^2}{1+{\rm cosh}\Big{[}\sqrt{\frac{2\pi^3}{27}}\frac{|(x
+      -x_{\rm b})^3|}{a\tau_0}\Big{]}}\Bigg{)}.
+\end{equation}
 
@@
 
-\bibliographystyle{latex/mn2e}
+\bibliographystyle{apj}
 \bibliography{references}

### 2014-12-18 RotacionOutFlows/Paper/ms.tex
New references in reference.bib file
cambios
fixes

@@
 
-\shortauthors{Remolina-Gutierrez, Forero-Romero \&Garavito-Camargo}
+\shortauthors{Remolina-Gutierrez, Forero-Romero \& Garavito-Camargo}
 
@@
 
-The Lyman-Alpha emission line is the spectral line produced when an electron goes from the second energy level to the first, loosing energy and emmiting it as light.
-When this energy decays are seen in Hydrogen atoms, the wavelenght of the \lya line is 121.567 nm.
-The detection of this emission line is a main tecnique in extragalactic astronomy because galaxies with a strong emission of this (called Lyman Alpha Emitters - LAEs) are used to study the evolution of the universe in big scale.
-\\
+The Lyman-Alpha emission line is the spectral line produced when an electron goes from the second energy level to the first,
+loosing energy and emmiting it as light. When this energy decays are seen in Hydrogen atoms, the wavelenght of the \lya line
+is 121.567 nm. The detection of this emission line is a main tecnique in extragalactic astronomy because galaxies with a
+strong emission of this (called Lyman Alpha Emitters - LAEs) are used to study the evolution of the universe in big scale. \\
 
-LAEs are young and far away galaxies with most of its matter composed by Hydrogen atoms, being the rest heavier elements, like Iron, produced by growing stars burning their material.
-Then, this spectral line tells very important information about the galaxy, most of it actually, which creates a motivation to find a way to model the \lya line according to certain free parameters that vary from a galaxy to another and that can be obtained from observations.
-\\
+LAEs are young and far away galaxies with most of its matter composed by Hydrogen atoms, being the rest heavier elements,
+like Iron, produced by growing stars burning their material. Then, this spectral line tells very important information about
+the galaxy, most of it actually, which creates a motivation to find a way to model the \lya line according to certain free
+parameters that vary from a galaxy to another and that can be obtained from observations. \\
 
-Our purpose in this paper is then to make a theoretical model, based on radiative transfer simulations, that use MonteCarlo computational methods to emulate how the line profile is going to come out of the galaxy if it is rotating and has a surrounding outflow, both of this phenomena characterized by key parameters that are going to be described further on the paper.
-\\
+Our purpose in this paper is then to make a theoretical model, based on radiative transfer simulations, that use MonteCarlo
+computational methods to emulate how the line profile is going to come out of the galaxy if it is rotating and has a surrounding
+outflow, both of this phenomena characterized by key parameters that are going to be described further on the paper. \\
 
@@
 
-As it has been described, the main purpose of this project is to mix a rotating galaxy with an external outflow surrounding it and analyze the resulting spectrum.
-The rotation model for the LAE consists on a sphere with an homogeneous mixture of dust and hydrogen at a constant temperature undergoing a solid-body rotation.
-The spectrum then depends on the maximum velocity of the sphere, the neutral hydrogen optical depths and the viewing angle.
-What happens is that photons are emmited from a central distribution of gas and escape the sphere after a radiative transfer process that ends at the border.\\
+As it has been described, the main purpose of this project is to mix a rotating galaxy with an external outflow surrounding
+it and analyze the resulting spectrum. The rotation model for the LAE consists on a sphere with an homogeneous mixture of
+dust and hydrogen at a constant temperature undergoing a solid-body rotation. The spectrum then depends on the maximum velocity
+of the sphere, the neutral hydrogen optical depths and the viewing angle. What happens is that photons are emmited from a central
+distribution of gas and escape the sphere after a radiative transfer process that ends at the border.\\
 
-In this model, rotation does not induce any spatial anisotropy in the integrated line flux, the escape fraction or the average number of scatterings, which led to the creation of an analytic approximation for the galaxy spectrum.
-This mathematical expression helps to minimize the computational costs and lets try with several parameters without spending great amounts of time running the code.
-\\
+In this model, rotation does not induce any spatial anisotropy in the integrated line flux, the escape fraction or the average
+number of scatterings, which led to the creation of an analytic approximation for the galaxy spectrum. This mathematical expression
+helps to minimize the computational costs and lets try with several parameters without spending great amounts of time running the code. \\
 
-After this photons escape the galaxy to empty space, they encounter a thin spherical shell of matter at a certain radius from the center.
-That material is the outflow of the LAE, created mainly by starbursts which composition is characterized with the parameters of Hydrogen column density and metallicity.
-Besides its components, the galactic outflow is also defined by an expanding constant velocity that affects the redshift of the photons.\\
+After this photons escape the galaxy to empty space, they encounter a thin spherical shell of matter at a certain radius from the
+center. That material is the outflow of the LAE, created mainly by starbursts which composition is characterized with the parameters
+of Hydrogen column density and metallicity. Besides its components, the galactic outflow is also defined by an expanding constant
+velocity that affects the redshift of the photons.\\
 
-As there is a lot of empty space inside the shell, it acts as a reflector of photons.
-This means, that when one wants to comes out it is most likely to bounce inside the sphere several times before finally escaping.
-However it is not likely that the photon comes back again inside the galaxy, which helps that the first process does not have to be repeated, and both stages can be treated as consecutive, not simultaneous.
-\\
+As there is a lot of empty space inside the shell, it acts as a reflector of photons. This means, that when one wants to comes out it
+is most likely to bounce inside the sphere several times before finally escaping. However it is not likely that the photon comes back
+again inside the galaxy, which helps that the first process does not have to be repeated, and both stages can be treated as consecutive,
+  not simultaneous. \\
 
@@
 rotation. In this case we take the angular velocity in the same
-direction as the $\hat{k}$ unit vector.
+direction as the $\hat{k}$ unit vector.\\
 
-In this work we use the analytical expression for rotation derived in [garavito-camargo et al]
-where a rotating sphere can be seen as a static sphere in the laboratory
-frame with a bulk velocity difference in each surface element with respect
+In this work we use the analytical expression for rotation derived in \citep{Garavito14} where a rotating sphere can be seen as a static sphere in the laboratory frame with a bulk velocity difference in each surface element with respect
 to a distant observer. With the previous analysis the outcoming spectra can be
@@
 
+\citep{Orsi12}
+
 ---------------------------------------------------------------------\\
@@
 - Important equations and description of the parameters\\
-- Why we use ThinShel instead of Wind. Its advantages (explains redshift, avoids re-difussion, bounces).\\
-- Ref: Alvaro and Julian\\
+- Why we use ThinShell instead of Wind. Its advantages (explains redshift, avoids re-difussion, bounces).\\
 -----------------------------------------------------------------------\\
@@
 MISSING IN REFERENCES: \\
-- A loooot of references not here yet.\\
 - Alvaro's paper.(Can galactic outflows explain the properties of Lyα emitters?
@@
 
-\bibliographystyle{apj}
+\bibliographystyle{latex/apj}
 \bibliography{references}

### 2015-01-19 RotacionOutFlows/Paper/ms.tex
avance

@@
 \include{latex/packages_commands}
-\usepackage{multirow,color,wrapfig,ulem}
-\usepackage{graphicx}
-\usepackage{graphics}
-\usepackage[dvips]{epsfig}
-\newcommand{\avg}[1]{\langle{#1}\rangle}
-\newcommand{\nscatt}{\langle N_{\rm  scatt}\rangle}
-\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha~}\else{Ly$\alpha$~}\fi}}
-\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}
-\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc }\fi}}
-\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}
-\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}
-\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm{M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}
-\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm{M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}
-\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}
-\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}
-%\newcommand{\lya}{{Lyman $\alpha$~}}
-\newcommand{\clara}{{\texttt{CLARA}}~}
-\newcommand{\rand}{{\ifmmode{{\mathcal{R}}}\else{${\mathcal{R}}$ }\fi}}
-\newcommand{\hs}{{\hspace{1mm}}}
-%\newcommand{\kms}{{\ifmmode{{\mathrm{\,km\ s}^{-1}}}\else{\,km~s$^{-1}$}\fi}}
 
@@
 
-\keywords{Lyman Alpha Emission,  ....MISSING....}
+\keywords{Lyman Alpha Emission, Galaxy Rotation, Galaxy Outflows ....MISSING....}
 
@@
 
-The Lyman-Alpha emission line is the spectral line produced when an electron goes from the second energy level to the first,
-loosing energy and emmiting it as light. When this energy decays are seen in Hydrogen atoms, the wavelenght of the \lya line
-is 121.567 nm. The detection of this emission line is a main tecnique in extragalactic astronomy because galaxies with a
-strong emission of this (called Lyman Alpha Emitters - LAEs) are used to study the evolution of the universe in big scale. \\
+The Lyman-Alpha emission line is the spectral line produced when an electron goes from the second energy level to the first, loosing energy and emitting it as light.
+When this energy decays are seen in Hydrogen atoms, the wavelength of the \lya line is 121.567 nm.
+The detection of this emission line is a main tecnique in extragalactic astronomy because galaxies with a strong emission of this (called Lyman Alpha Emitters - LAEs) are used to study the evolution of the universe in big scale.
+\\
 
-LAEs are young and far away galaxies with most of its matter composed by Hydrogen atoms, being the rest heavier elements,
-like Iron, produced by growing stars burning their material. Then, this spectral line tells very important information about
-the galaxy, most of it actually, which creates a motivation to find a way to model the \lya line according to certain free
-parameters that vary from a galaxy to another and that can be obtained from observations. \\
+LAEs are young and far away galaxies with most of its matter composed by Hydrogen atoms, being the rest heavier elements, like Iron, produced by growing stars burning their material.
+Then, this spectral line tells very important information about the galaxy, most of it actually, which creates a motivation to find a way to model the \lya line according to certain free parameters that vary from a galaxy to another and that can be obtained from observations.
+\\
 
@@
 
-As it has been described, the main purpose of this project is to mix a rotating galaxy with an external outflow surrounding
-it and analyze the resulting spectrum. The rotation model for the LAE consists on a sphere with an homogeneous mixture of
-dust and hydrogen at a constant temperature undergoing a solid-body rotation. The spectrum then depends on the maximum velocity
-of the sphere, the neutral hydrogen optical depths and the viewing angle. What happens is that photons are emmited from a central
-distribution of gas and escape the sphere after a radiative transfer process that ends at the border.\\
+As it has been described, the main purpose of this project is to mix a rotating galaxy with an external outflow surrounding it and analyze the resulting spectrum.
+The rotation model for the LAE consists on a sphere with an homogeneous mixture of dust and hydrogen at a constant temperature undergoing a solid-body rotation.
+The spectrum then depends on the maximum velocity of the sphere, the neutral hydrogen optical depths and the viewing angle.
+What happens is that photons are emitted from a central distribution of gas and escape the sphere after a radiative transfer process that ends at the border.\\
 
@@
 After this photons escape the galaxy to empty space, they encounter a thin spherical shell of matter at a certain radius from the
-center. That material is the outflow of the LAE, created mainly by starbursts which composition is characterized with the parameters
-of Hydrogen column density and metallicity. Besides its components, the galactic outflow is also defined by an expanding constant
-velocity that affects the redshift of the photons.\\
+center.
+That material is the outflow of the LAE, created mainly by starbursts which composition is characterized with the parameters of Hydrogen column density and metallicity.
+Besides its components, the galactic outflow is also defined by an expanding constant velocity that affects the redshift of the photons.\\
 
-As there is a lot of empty space inside the shell, it acts as a reflector of photons. This means, that when one wants to comes out it
-is most likely to bounce inside the sphere several times before finally escaping. However it is not likely that the photon comes back
-again inside the galaxy, which helps that the first process does not have to be repeated, and both stages can be treated as consecutive,
-  not simultaneous. \\
+As there is a lot of empty space inside the shell, it acts as a reflector of photons.
+This means, that when one wants to comes out it is most likely to bounce inside the sphere several times before finally escaping.
+However it is not likely that the photon comes back again inside the galaxy, which helps that the first process does not have to be repeated, and both stages can be treated as consecutive, not simultaneous.
+\\
 
@@
 \label{sec:theo}
-In this section we describe the two different models that are used in this project,
-that are able to reproduce a real and consistent \lya profile. As first we implement
-the rotation followed by an outflow.\\
-
----------------------------------------------------------------------\\
-MISSING: \\
-- Express prettier the intro of the section\\
------------------------------------------------------------------------\\
+In this section we describe the two different models that together are used to reproduce a real and consistent \lya profile.
+The first one is a rotation model for the galaxy and the second is a thin shell model for the outflow.
+\\
 
@@
 
-We use the simplified rotation model developed by [garavito-camargo et al]
-in which a rotating galaxy is modeled as a solid rotating sphere, with a homogeneous mixture
-of hydrogen and dust. Photons can be initially at the center or can be
-homogeneously distributed inside the sphere. The equations governing this
- solid-body rotation sphere in which the axys of rotation is defined to be allign
- with the $z$-axys are:
+We use the simplified rotation model developed by \citep{Garavito14} in which a rotating galaxy is modeled as a solid rotating sphere, with a homogeneous mixture of hydrogen and dust.
+Photons can be initially at the center or can be homogeneously distributed inside the sphere.
+The equations governing this solid-body rotation sphere in which the axis of rotation is defined to be align with the $z$-axis are:
 
@@
 \end{equation}
+
 \begin{equation}
@@
 \end{equation}
-%
 
-Where $R$ is the radius of the sphere and $V_{\rm max}$ is the linear
-velocity at the sphere's surface. The minus/plus sign in the
-$x$/$y$-component of the velocity indicates the direction of
-rotation. In this case we take the angular velocity in the same
-direction as the $\hat{k}$ unit vector.\\
+Where $R$ is the radius of the sphere and $V_{\rm max}$ is the linear velocity at the sphere's surface.
+The minus/plus sign in the $x$/$y$-component of the velocity indicates the direction of rotation.
+In this case we take the angular velocity in the same direction as the $\hat{k}$ unit vector.\\
 
 In this work we use the analytical expression for rotation derived in \citep{Garavito14} where a rotating sphere can be seen as a static sphere in the laboratory frame with a bulk velocity difference in each surface element with respect
-to a distant observer. With the previous analysis the outcoming spectra can be
-expressed as:
+to a distant observer. With the previous analysis the outcoming spectra can be expressed as:
 
@@
 
-Where $J(x, b, \phi, i)$ is the spectrum of the flux emerging from the
-surface at point $(b, \phi)$ and is expressed as:
+Where $J(x, b, \phi, i)$ is the spectrum of the flux emerging from the surface at point $(b, \phi)$ and is expressed as:
 
 \begin{equation}
-J(x,b,\phi,i)=\frac{\sqrt{\pi}}{\sqrt{24}a\tau_0}\Bigg{(}\frac{(x-x_{\rm
-    b})^2}{1+{\rm cosh}\Big{[}\sqrt{\frac{2\pi^3}{27}}\frac{|(x
-      -x_{\rm b})^3|}{a\tau_0}\Big{]}}\Bigg{)}.
+J(x,b,\phi,i)=\frac{\sqrt{\pi}}{\sqrt{24}a\tau_0}\Bigg{(}\frac{(x-x_{\rm b})^2}{1+{\rm cosh}\Big{[}\sqrt{\frac{2\pi^3}{27}}\frac{|(x-x_{\rm b})^3|}{a\tau_0}\Big{]}}\Bigg{)}
 \end{equation}
@@
 
-\citep{Orsi12}
+We use the outflow model stated in \citep{Orsi12} in which the outflow consists of a homogeneous, expanding, isothermal spherical shell surrounding a central galaxy.
+The inner radius $R_{in}$ is related to the outer radius $R_{out}$ by the expression $R_{in} = f_{th}R_{out}$, where $f_{th}=0.9$.
+The temperature of the medium is assumed constant and equal to $T=10^4 K$ and it is expanding at a constant velocity \vel.
+This outflow is composed by dust and gas uniformly mixed described by the column density \nh and the metallicity $Z$ as follows:
 
----------------------------------------------------------------------\\
-MISSING:\\
-- Important equations and description of the parameters\\
-- Why we use ThinShell instead of Wind. Its advantages (explains redshift, avoids re-difussion, bounces).\\
------------------------------------------------------------------------\\
+\begin{equation}
+\label{eq:nh}
+n_H = \frac{X_H M_{shell}}{4\pi m_H {R^2}_{out}}
+\end{equation}
+
+Where $M_{shell}$ is the mass of the outflow, $m_H$ is the mass of the hydrogen atom and $X_H=0.74$ is the fraction of hydrogen in the cold gas.
+
+\begin{equation}
+\label{eq:z}
+Z = f_Z \langle Z_{cold} \rangle
+\end{equation}
+
+Where $\langle Z_{cold} \rangle$ is the average metallicity of the cold gas and it is weighted by the product of the mass of cold gas and the \lya luminosity of the disc and bulge $f_Z$. \\
+
+We decided to choose this model for two main reasons.
+First, when we analyze observed spectra we can se that the line is spread around the place where line should be when already taking into account the redshift due to the distance to the LAE.
+This implies that the photons before escaping the composed system suffer a change in frequency themselves, which we explain by making them rebound over the inner surface of the shell such as some of them suffer blueshift and other redshift, that even small, is significant and observed.\\
+
+The second reason is because as the space between the shell and the galaxy is said to be void, the photons that escape from it suffer the scattering process at a far distance from the center, in a way such as if they rebound the chances that it happens in the normal direction to the surface are lower than in any other model.
+This implies that the photons are less likely to re-enter the galaxy so there is no need to start the diffusion inside again, allowing us to divide the spectrum creation process into 2 independent events, saving computational time and simplifying the model to its best.
+\\
 
@@
 
----------------------------------------------------------------------\\
-MISSING: \\
-- Full explanation.\\
-- How exactly are this 2 mixed\\
-- Tell and make a detailed explanation of the free parameters that we are going to explore. \\
-- State the fixed parameters.\\
------------------------------------------------------------------------\\
+The joint model consists of combining the two models that were just explained.
+A rotating spherical galaxy is placed at the center with a thin shell outflow surrounding it.
+What happens is that the photons that escaped the galaxy enter now into the outflow with the same radial direction that they came out with.
+At the end only a fraction of those manage to get out of the outflow and their wavelengths are measured to find the final spectrum.\\
+
+In order to simulate all the possible cases we set some key parameters for the program to vary, and some others fixed which are defined by the characteristics of LAEs. This are chosen as follows.\\
+
+\subsubsection{Fixed Parameters}
+
+For the first stage there are two fixed parameters: the optical depth $\tau = 10^8$ and the galaxy rotation velocity $v_{gal}=100$ \kms.
+For the second stage there is one fixed parameter: the metallicity of the outflow $Z=-4.0$.
+This 3 fixed values are selected because the characteristics of observed LAEs, especially their low mass and their highest star formation rate of all.\\
+
+\subsubsection{Free Parameters}
+
+We have then 3 parameters left that are going to vary along a wide range. These are: the galaxy viewing angle \ang, the hydrogen column density \nh and the outflow expanding velocity \vel. \\
+
+\ang covers 3 different angles: $0^\circ$, $45^\circ$ and $90^\circ$.
+\lognh takes 41 different values from 20.0 to 22.5.
+And \vel covers 5 equidistant velocities from 100 \kms to 500 \kms.
+The permutations of these three are analyzed in section \ref{sec:results}.
 
@@
 However this change is not that significant.
-The resulting spectrums are completely the same, but enlarged vertically by a small factor.
+The resulting spectra are completely the same, but enlarged vertically by a small factor.
 Fig.
@@
 \begin{center}
-  \includegraphics[width=0.4\textwidth]{./figures/influence_ang.png}
+  \includegraphics[width=0.5\textwidth]{./figures/influence_ang.png}
 \end{center}
@@
 
-\subsubsection{Influence of the Hydrogen Column Density: \lognh }
+\subsubsection{Influence of the Outflow Hydrogen Column Density: \lognh }
 
 The effect of the \lognh is the creation of 2 peaks: the left one very thin, tall and pronounced, and the right one very wide, small and soften.
-When the $log{nH}$ is increased, the left peak starts to decrease while mixing with the right one, decreasing their height ratio until the left peak completely dissapears.
+When the $log{nH}$ is increased, the left peak starts to decrease while mixing with the right one, decreasing their height ratio until the left peak completely disappears.
 The resulting spectrum, with high column density, is a wide single mountain with intensity significantly less than at the beginning.
@@
 \begin{center}
-  \includegraphics[width=0.4\textwidth]{./figures/influence_lognH.png}
+  \includegraphics[width=0.5\textwidth]{./figures/influence_lognH.png}
 \end{center}
-\caption{\textbf{Influence of Hydrogen Column Density:} The values of the fixed parameters are \vel = 100 \kms and \ang = 90$^\circ$.
+\caption{\textbf{Influence of Outflow Hydrogen Column Density:} The values of the fixed parameters are \vel = 100 \kms and \ang = 90$^\circ$.
 There are three stages of the \lognh value shown: initial, intermediate and final, with the values shown on the plot.\\
@@
 -----------------------------------------------------------------------\\
+
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.5\textwidth]{./figures/influence_vel.png}
+\end{center}
+\caption{\textbf{Influence of Outflow Expanding Velocity:} The values of the fixed parameters are \lognh = 20.0625 and \ang = 90$^\circ$. MISSIIIIIIING.\\
+\label{fig:influence_vel}}
+\end{figure}
 
@@
 
-The decrease of the intensity while increasing the column density is caused because the column density is proportional to the absortion of light in the gas.
-The more $log{nH}$, the less photons get out of the outflow.
+The decrease of the intensity while increasing the column density is caused because the second is proportional to the absorption of light in the gas.
+The more \lognh, the less photons get out of the outflow.
 
@@
 
----------------------------------------------------------------------\\
-MISSING IN REFERENCES: \\
-- Alvaro's paper.(Can galactic outflows explain the properties of Lyα emitters?
-Alvaro Orsi, Cedric G. Lacey and Carlton M. Baugh)\\
-- Use the correct citation method. \\
------------------------------------------------------------------------\\
-
 \bibliographystyle{latex/apj}
@@
 %\section{Ejemplos para tener en cuenta}
-%\label{sec:implementation}
-%
-%Ejemplo de ecuacion
-%
-%\begin{equation}
-%    v_{x}=-\frac{y}{R}V_{\rm max}, \label{subeq1}
-%\end{equation}
-%
-%Ejemplo referencia a figura
-%
-%In Fig. \ref{fig:geometry} se ve .....
 %

### 2015-02-02 RotacionOutFlows/Paper/ms.tex
more

@@
 The joint model consists of combining the two models that were just explained.
-A rotating spherical galaxy is placed at the center with a thin shell outflow surrounding it.
+A rotating spherical galaxy is placed at the center with a thin shell outflow surrounding it as seen in Fig.
+\ref{fig:model}.
 What happens is that the photons that escaped the galaxy enter now into the outflow with the same radial direction that they came out with.
 At the end only a fraction of those manage to get out of the outflow and their wavelengths are measured to find the final spectrum.\\
+
+\begin{figure}[h!]
+\begin{center}
+  \includegraphics[width=0.3\textwidth]{./figures/model.png}
+\end{center}
+\caption{\textbf{Model:} A central rotating galaxy surrounded by an expanding thin shell outflow.\\
+\label{fig:model}}
+\end{figure}
 
@@
 \label{sec:results}
-Here goes the results....
+
+The results of this project consist of emulating a LAE spectrum basing on its physical characteristics defined by the 3 free parameters we stated before.
+When defined the combination of those three.
+\\
 
@@
 - What are the compact results.\\
-- Some plots.\\
 - Not a physical analysis yet. \\
@@
 -----------------------------------------------------------------------\\
+
+In the following subsection each free parameter is explained deeper. \\
 
@@
 Fig.
-\ref{fig:influence_ang} helps visualize this effect in a better way.\\
+\ref{fig:influence_ang} helps visualize this effect in a better way.
 
-\begin{figure}
+\begin{figure}[h!]
 \begin{center}
@@
 Fig.
-\ref{fig:influence_lognH} helps visualize this effect in a better way.\\
+\ref{fig:influence_lognH} helps visualize this effect in a better way.
 
-\begin{figure}
+\begin{figure}[h!]
 \begin{center}
@@
 
----------------------------------------------------------------------\\
-MISSING: \\
-- Influence Outflow Velocity.\\
------------------------------------------------------------------------\\
+The effect of this parameter consists in a shift of the initial spectrum in the column density.
+The more \vel the outflow has, the more the spectrum simulates the previous velocity but with a greater \lognh.
+If one compares with Fig.
+\ref{fig:influence_lognH} the similarities are really clear.
 
-\begin{figure}
+\begin{figure}[h!]
 \begin{center}
@@
 \end{center}
-\caption{\textbf{Influence of Outflow Expanding Velocity:} The values of the fixed parameters are \lognh = 20.0625 and \ang = 90$^\circ$. MISSIIIIIIING.\\
+\caption{\textbf{Influence of Outflow Expanding Velocity:} The values of the fixed parameters are \lognh = 20.0625 and \ang = 90$^\circ$.
+If one increases \lognh for an outflow with \vel = 100 \kms it will create similar spectra to these in certain points.\\
 \label{fig:influence_vel}}
@@
 
-To ...\\
+We acknowledge Alvaro Orsi and Julian Mejia for collaborating with us offering their time, advice and especially data. We used their outflow simulations in order to get our results.\\
 
-The data, source code and instructions to
-replicate the results of this paper can be found
-here {\texttt{https://github.com/mariacamilaremolinagutierrez/ LymanAlpha/}}.
-Most of our code benefits from the work of the IPython and Matplotlib
-communities \citep{IPython,matplotlib}.\\
+The data, source code and instructions to replicate the results of this paper can be found here {\texttt{https://github.com/mariacamilaremolinagutierrez/ LymanAlpha/}}.
+Most of our code benefits from the work of the IPython and Matplotlib communities \citep{IPython,matplotlib}.\\
 
@@
 MISSING: \\
-- Help from Alvaro and Julian: data, explanations, advice and collaboration. \\
-- Soooo many more acknowledgments.\\
+- More acknowledgments.\\
 -----------------------------------------------------------------------\\

### 2015-02-10 RotacionOutFlows/Paper/ms.tex
Intro first draft, still missing references and additional info

@@
 
-\author{ Maria Camila Remolina-Gutierrez, Jaime E. Forero-Romero, Juan N. Garavito-Camargo}
+\author{ Maria Camila Remolina-Gutierrez, Jaime E. Forero-Romero \& Juan N. Garavito-Camargo}
 \affil{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
@@
 
-\keywords{Lyman Alpha Emission, Galaxy Rotation, Galaxy Outflows ....MISSING....}
+\keywords{Galaxies: high-redshift, Lyman Alpha Emission, Galaxy Rotation, Galaxy Outflows ....MISSING....}
 
@@
 
-The Lyman-Alpha emission line is the spectral line produced when an electron goes from the second energy level to the first, loosing energy and emitting it as light.
-When this energy decays are seen in Hydrogen atoms, the wavelength of the \lya line is 121.567 nm.
-The detection of this emission line is a main tecnique in extragalactic astronomy because galaxies with a strong emission of this (called Lyman Alpha Emitters - LAEs) are used to study the evolution of the universe in big scale.
-\\
+In 1967 \cite{PartridgePeebles} predicted a population of galaxies with a strong 
+Lyman Alpha (\lya) emission,  nowadays galaxies who are selected using the \lya 
+line are known as Lyman Alpha Emitters (LAEs). Since the first 
+observed LAE by \cite{DjorgovskiThompson} different teams have 
+observed several LAEs \cite{Kulas12, Ostlin14}  ,  become a very important tool to 
+explore the extragalactic Universe $cite{}$.  Specially at $z>=2$ since it is when the 
+line is redshifted into the optical regime. it is specially useful to study the 
+properties of the high redshift Universe, such as the large scale structure.
+and new projects are beeing planned for the near future $\cite{}$.
 
-LAEs are young and far away galaxies with most of its matter composed by Hydrogen atoms, being the rest heavier elements, like Iron, produced by growing stars burning their material.
+A variety of Astrophysical problems can be studied using LAEs; clustering
+of galaxies at high redshift, Interstellar (ISM) and intergalactic (IGM) medium 
+properties and cosmological reionization among others. This motivates to study in 
+detail the processes that model the morphology of the \lya line.
+
+To fully understand the observed spectra of LAEs this galaxies must be modeled.
+however the resonant nature of the lines makea this a challenging task. 
+Neufeld et 90 the outcoming spectra of galaxies through static mediums 
+Recent hydrodynamical simulations have been explored the properties of the IGM/ISM 
+in large scale simulations, while some others have studied detailed galaxies. 
+On the other hand RT computations have been in order to understand the effect of the 
+gas kinematics in the Line, special attention have been devoted to model the presence 
+of outflows in the galaxy. here different models have attempt to (name the models, shell cavities etc.)
+. Most recently \cite{Garavito14} have studied in detail the effect 
+of rotation on the lyman alpha line.
+
+As many previous studies have shown outflows are present in LAEs (\textbf{References}),
+the outflows are mainly a consecuence of the intergalactic medium (IGM) being ejected 
+from the galaxy due to supernova explotions.
+However rotation should also be present in this galaxies. The joint effect of the two 
+above properties should have a direct effect on the morphology of the \lya line.
+
+This effect is the motivation of this paper in which we combine the effect of rotation 
+follow by an outflow. We proposed a simplyfied model in which the galaxy is modeled
+as an sphere, with an homogeneous mixture of dust and hydrogen at a constant temperature
+and undergoing solid-body rotation.
+
+The solid-body rotation does not induce any spatial anisotropy in the integrated line flux, 
+the escape fraction or in the average number of scatterings. This symmetry allows 
+to the creation of an analytic approximation for the galaxy spectrum 
+proposed, see \cite{Garavito14} for details. In this model the optical depth $\tau_{H}$, the 
+rotation velocity $V_{max}$ and the inclination angle $\theta$ are free parameters.
+
+The outcoming spectra of the rotating galaxy is then affected by a symmetric thin shell of expanding
+gas at a constant velocity following the model proposed by \cite{2014arXiv1404.2958V, Orsi12}.
+
+This paper is structured as follows. In \S \ref{sec:theo} we explain in detail the model of rotation
+and outflow that we use as well of our joint model (Rotation \& Outflow). In \S \ref{sec:results} we present
+the results of our model. In \S \ref{sec:discussion} we compare our results with 
+recent observations of LAEs with special attention of those morphologies that present
+features of galaxy rotation and outflows. In the latest section we present our 
+conclutions.
+
+%LAEs are young and far away galaxies with most of its matter composed by Hydrogen atoms, being the rest heavier elements, like Iron, produced by growing stars burning their material.
 Then, this spectral line tells very important information about the galaxy, most of it actually, which creates a motivation to find a way to model the \lya line according to certain free parameters that vary from a galaxy to another and that can be obtained from observations.
@@
 
-Our purpose in this paper is then to make a theoretical model, based on radiative transfer simulations, that use MonteCarlo
-computational methods to emulate how the line profile is going to come out of the galaxy if it is rotating and has a surrounding
-outflow, both of this phenomena characterized by key parameters that are going to be described further on the paper. \\
+%Our purpose in this paper is then to make a theoretical model, based on radiative transfer simulations, that use MonteCarlo
+%computational methods to emulate how the line profile is going to come out of the galaxy if it is rotating and has a surrounding
+%outflow, both of this phenomena characterized by key parameters that are going to be described further on the paper. \\
 
----------------------------------------------------------------------\\
-MISSING: What has been done related to this?\\
------------------------------------------------------------------------\\
-
-As it has been described, the main purpose of this project is to mix a rotating galaxy with an external outflow surrounding it and analyze the resulting spectrum.
+%As it has been described, the main purpose of this project is to mix a rotating galaxy with an external outflow surrounding it and analyze the resulting spectrum.
 The rotation model for the LAE consists on a sphere with an homogeneous mixture of dust and hydrogen at a constant temperature undergoing a solid-body rotation.
@@
 
-In this model, rotation does not induce any spatial anisotropy in the integrated line flux, the escape fraction or the average
-number of scatterings, which led to the creation of an analytic approximation for the galaxy spectrum. This mathematical expression
-helps to minimize the computational costs and lets try with several parameters without spending great amounts of time running the code. \\
+%In this model, rotation does not induce any spatial anisotropy in the integrated line flux, the escape fraction or the average
+%number of scatterings, which led to the creation of an analytic approximation for the galaxy spectrum. This mathematical expression
+%helps to minimize the computational costs and lets try with several parameters without spending great amounts of time running the code. \\
 
-After this photons escape the galaxy to empty space, they encounter a thin spherical shell of matter at a certain radius from the
-center.
+%After this photons escape the galaxy to empty space, they encounter a thin spherical shell of matter at a certain radius from the
+%center.
 That material is the outflow of the LAE, created mainly by starbursts which composition is characterized with the parameters of Hydrogen column density and metallicity.
@@
 
-As there is a lot of empty space inside the shell, it acts as a reflector of photons.
+%As there is a lot of empty space inside the shell, it acts as a reflector of photons.
 This means, that when one wants to comes out it is most likely to bounce inside the sphere several times before finally escaping.

### 2015-02-10 RotacionOutFlows/Paper/ms.tex
a couple of references

@@
 of galaxies at high redshift, Interstellar (ISM) and intergalactic (IGM) medium 
-properties and cosmological reionization among others. This motivates to study in 
+properties and cosmological reionization for a recent review see \cite{review} 
+among others. This motivates to study in 
 detail the processes that model the morphology of the \lya line.
@@
 however the resonant nature of the lines makea this a challenging task. 
-Neufeld et 90 the outcoming spectra of galaxies through static mediums 
+\cite{Neufeld90} the outcoming spectra of galaxies through static mediums 
 Recent hydrodynamical simulations have been explored the properties of the IGM/ISM 

### 2015-02-11 RotacionOutFlows/Paper/ms.tex
minor changes

@@
 
-In 1967 \cite{PartridgePeebles} predicted a population of galaxies with a strong 
+\cite{PartridgePeebles} predicted a population of galaxies with a strong 
 Lyman Alpha (\lya) emission,  nowadays galaxies who are selected using the \lya 
@@
 observed LAE by \cite{DjorgovskiThompson} different teams have 
-observed several LAEs \cite{Kulas12, Ostlin14}  ,  become a very important tool to 
-explore the extragalactic Universe $cite{}$.  Specially at $z>=2$ since it is when the 
-line is redshifted into the optical regime. it is specially useful to study the 
-properties of the high redshift Universe, such as the large scale structure.
-and new projects are beeing planned for the near future $\cite{}$.
+observed several LAEs \cite{Kulas12, Ostlin14} with the aim of  
+exploring the extragalactic Universe $cite{}$.  Specially at $z>=2$ since it is when the 
+line is redshifted into the optical regime. With the outcoming of new and powerfull telescopes
+such as the James Webb Space Telescope new LAEs are going to be discovered.
 
@@
 To fully understand the observed spectra of LAEs this galaxies must be modeled.
-however the resonant nature of the lines makea this a challenging task. 
-\cite{Neufeld90} the outcoming spectra of galaxies through static mediums 
-Recent hydrodynamical simulations have been explored the properties of the IGM/ISM 
+However the resonant nature of the lines makes this a challenging task. 
+Analytical solutions for the outcoming spectra in simple ISM static geometries have been dereived
+\cite{Neufeld90}. Recent hydrodynamical simulations have studied the outcomming spectra of LAEs
 in large scale simulations, while some others have studied detailed galaxies. 
-On the other hand RT computations have been in order to understand the effect of the 
+Radiative transfer codes have been used in order to understand the effect of the 
 gas kinematics in the Line, special attention have been devoted to model the presence 

### 2015-02-11 RotacionOutFlows/Paper/ms.tex
more references

@@
 observed LAE by \cite{DjorgovskiThompson} different teams have 
-observed several LAEs \cite{Kulas12, Ostlin14} with the aim of  
+observed several LAEs \cite{Kulas12, Yamada2012, Chonis2013,Finkelstein2013,Ostlin14} with the aim of  
 exploring the extragalactic Universe $cite{}$.  Specially at $z>=2$ since it is when the 
@@
 
-A variety of Astrophysical problems can be studied using LAEs; clustering
+A variety of Astrophysical problems can be studied using LAEs; clustering \citep{Behrens13}
 of galaxies at high redshift, Interstellar (ISM) and intergalactic (IGM) medium 
-properties and cosmological reionization for a recent review see \cite{review} 
+properties \citep{DijkstraKramer} and cosmological reionization for a recent review see \cite{review} 
 among others. This motivates to study in 
@@
 Analytical solutions for the outcoming spectra in simple ISM static geometries have been dereived
-\cite{Neufeld90}. Recent hydrodynamical simulations have studied the outcomming spectra of LAEs
-in large scale simulations, while some others have studied detailed galaxies. 
-Radiative transfer codes have been used in order to understand the effect of the 
+\cite{Adams72, Harrington73, Neufeld90, Dijkstra06}. Recent hydrodynamical simulations have studied the outcomming spectra of LAEs
+in large scale simulations, while some others have studied detailed galaxies \citep{Verhamme12}. 
+Radiative transfer codes \citep{Laursen09, Verhamme06, CLARA}have been used in order to understand the effect of the 
 gas kinematics in the Line, special attention have been devoted to model the presence 
 of outflows in the galaxy. here different models have attempt to (name the models, shell cavities etc.)
+\citep{Behrens2014}
 . Most recently \cite{Garavito14} have studied in detail the effect 

### 2015-02-25 RotacionOutFlows/Paper/ms.tex
changing line endings, fixing long lines, starting to refine the outflow model description

@@
 observed LAE by \cite{DjorgovskiThompson} different teams have 
-observed several LAEs \cite{Kulas12, Yamada2012, Chonis2013,Finkelstein2013,Ostlin14} with the aim of  
-exploring the extragalactic Universe $cite{}$.  Specially at $z>=2$ since it is when the 
-line is redshifted into the optical regime. With the outcoming of new and powerfull telescopes
-such as the James Webb Space Telescope new LAEs are going to be discovered.
+observed several LAEs \cite{Kulas12, Yamada2012,
+  Chonis2013,Finkelstein2013,Ostlin14} with the aim of   exploring the
+extragalactic Universe $cite{}$.  Specially at $z>=2$ since it is when
+the  line is redshifted into the optical regime. With the outcoming of
+new and powerfull telescopes such as the James Webb Space Telescope
+new LAEs are going to be discovered.
 
-A variety of Astrophysical problems can be studied using LAEs; clustering \citep{Behrens13}
-of galaxies at high redshift, Interstellar (ISM) and intergalactic (IGM) medium 
-properties \citep{DijkstraKramer} and cosmological reionization for a recent review see \cite{review} 
-among others. This motivates to study in 
+A variety of Astrophysical problems can be studied using LAEs;
+clustering \citep{Behrens13} of galaxies at high redshift,
+Interstellar (ISM) and intergalactic (IGM) medium  properties
+\citep{DijkstraKramer} and cosmological reionization for a recent
+review see \cite{review}  among others. This motivates to study in
 detail the processes that model the morphology of the \lya line.
 
-To fully understand the observed spectra of LAEs this galaxies must be modeled.
-However the resonant nature of the lines makes this a challenging task. 
-Analytical solutions for the outcoming spectra in simple ISM static geometries have been dereived
-\cite{Adams72, Harrington73, Neufeld90, Dijkstra06}. Recent hydrodynamical simulations have studied the outcomming spectra of LAEs
-in large scale simulations, while some others have studied detailed galaxies \citep{Verhamme12}. 
-Radiative transfer codes \citep{Laursen09, Verhamme06, CLARA}have been used in order to understand the effect of the 
-gas kinematics in the Line, special attention have been devoted to model the presence 
-of outflows in the galaxy. here different models have attempt to (name the models, shell cavities etc.)
-\citep{Behrens2014}
-. Most recently \cite{Garavito14} have studied in detail the effect 
+To fully understand the observed spectra of LAEs this galaxies must be
+modeled. 
+However the resonant nature of the lines makes this a challenging
+task.  
+Analytical solutions for the outcoming spectra in simple ISM static
+geometries have been derived \cite{Adams72, Harrington73, Neufeld90,
+  Dijkstra06}. Recent hydrodynamical simulations have studied the
+outcomming spectra of LAEs in large scale simulations, while some
+others have studied detailed galaxies \citep{Verhamme12}.  
+Radiative transfer codes \citep{Laursen09, Verhamme06, CLARA}have been
+used in order to understand the effect of the  gas kinematics in the
+Line, special attention have been devoted to model the presence   of
+outflows in the galaxy. here different models have attempt to (name
+the models, shell cavities etc.) 
+\citep{Behrens2014}. 
+Most recently \cite{Garavito14} have studied in detail the effect 
 of rotation on the lyman alpha line.
 
-As many previous studies have shown outflows are present in LAEs (\textbf{References}),
-the outflows are mainly a consecuence of the intergalactic medium (IGM) being ejected 
-from the galaxy due to supernova explotions.
-However rotation should also be present in this galaxies. The joint effect of the two 
-above properties should have a direct effect on the morphology of the \lya line.
+As many previous studies have shown outflows are present in LAEs
+(\textbf{References}), the outflows are mainly a consecuence of the
+intergalactic medium (IGM) being ejected  from the galaxy due to
+supernova explotions. 
+However rotation should also be present in this galaxies. The joint
+effect of the two above properties should have a direct effect on the
+morphology of the \lya line.
 
-This effect is the motivation of this paper in which we combine the effect of rotation 
-follow by an outflow. We proposed a simplyfied model in which the galaxy is modeled
-as an sphere, with an homogeneous mixture of dust and hydrogen at a constant temperature
-and undergoing solid-body rotation.
+This effect is the motivation of this paper in which we combine the
+effect of rotation  follow by an outflow. We proposed a simplyfied
+model in which the galaxy is modeled as an sphere, with an homogeneous
+mixture of dust and hydrogen at a constant temperature and undergoing
+solid-body rotation.
 
-The solid-body rotation does not induce any spatial anisotropy in the integrated line flux, 
-the escape fraction or in the average number of scatterings. This symmetry allows 
-to the creation of an analytic approximation for the galaxy spectrum 
-proposed, see \cite{Garavito14} for details. In this model the optical depth $\tau_{H}$, the 
-rotation velocity $V_{max}$ and the inclination angle $\theta$ are free parameters.
+The solid-body rotation does not induce any spatial anisotropy in the
+integrated line flux,  the escape fraction or in the average number of
+scatterings. This symmetry allows  to the creation of an analytic
+approximation for the galaxy spectrum  proposed, see \cite{Garavito14}
+for details. In this model the optical depth $\tau_{H}$, the  rotation
+velocity $V_{max}$ and the inclination angle $\theta$ are free
+parameters.
 
 The outcoming spectra of the rotating galaxy is then affected by a symmetric thin shell of expanding
-gas at a constant velocity following the model proposed by \cite{2014arXiv1404.2958V, Orsi12}.
+gas at a constant velocity following the model proposed by
+\cite{2014arXiv1404.2958V, Orsi12}.
 
 This paper is structured as follows. In \S \ref{sec:theo} we explain in detail the model of rotation
-and outflow that we use as well of our joint model (Rotation \& Outflow). In \S \ref{sec:results} we present
-the results of our model. In \S \ref{sec:discussion} we compare our results with 
-recent observations of LAEs with special attention of those morphologies that present
-features of galaxy rotation and outflows. In the latest section we present our 
-conclutions.
+and outflow that we use as well of our joint model (Rotation \&
+Outflow). In \S \ref{sec:results} we present  the results of our
+model. In \S \ref{sec:discussion} we compare our results with  recent
+observations of LAEs with special attention of those morphologies that
+present features of galaxy rotation and outflows. In the latest
+section we present our  conclutions.
 
@@
 \label{sec:theo}
-In this section we describe the two different models that together are used to reproduce a real and consistent \lya profile.
-The first one is a rotation model for the galaxy and the second is a thin shell model for the outflow.
-\\
+In this section we describe the two different models that together are
+used to reproduce a real and consistent \lya profile. The first one is
+a rotation model for the galaxy and the second is a thin shell model
+for the outflow. \\
 
@@
 
-Where $R$ is the radius of the sphere and $V_{\rm max}$ is the linear velocity at the sphere's surface.
-The minus/plus sign in the $x$/$y$-component of the velocity indicates the direction of rotation.
-In this case we take the angular velocity in the same direction as the $\hat{k}$ unit vector.\\
+Where $R$ is the radius of the sphere and $V_{\rm max}$ is the linear
+velocity at the sphere's surface. The minus/plus sign in the
+$x$/$y$-component of the velocity indicates the direction of
+rotation. In this case we take the angular velocity in the same
+direction as the $\hat{k}$ unit vector.
 
-In this work we use the analytical expression for rotation derived in \citep{Garavito14} where a rotating sphere can be seen as a static sphere in the laboratory frame with a bulk velocity difference in each surface element with respect
-to a distant observer. With the previous analysis the outcoming spectra can be expressed as:
+In this work we use the analytical expression for rotation derived in
+\citep{Garavito14} where a rotating sphere can be seen as a static
+sphere in the laboratory frame with a bulk velocity difference in each
+surface element with respect 
+to a distant observer. 
+With the previous analysis the outcoming spectra can be expressed as:
 
@@
 
-Where $J(x, b, \phi, i)$ is the spectrum of the flux emerging from the surface at point $(b, \phi)$ and is expressed as:
+Where $J(x, b, \phi, i)$ is the spectrum of the flux emerging from the
+surface at point $(b, \phi)$ and is expressed as:
 
@@
 
-\subsection{Outflow Model: ThinShell}
+\subsection{Outflow Model: Thin Shell}
 
-We use the outflow model stated in \citep{Orsi12} in which the outflow consists of a homogeneous, expanding, isothermal spherical shell surrounding a central galaxy.
-The inner radius $R_{in}$ is related to the outer radius $R_{out}$ by the expression $R_{in} = f_{th}R_{out}$, where $f_{th}=0.9$.
-The temperature of the medium is assumed constant and equal to $T=10^4 K$ and it is expanding at a constant velocity \vel.
-This outflow is composed by dust and gas uniformly mixed described by the column density \nh and the metallicity $Z$ as follows:
+We use the outflow model stated in \citep{Orsi12}. 
+In their model the outflow consists of an homogeneous, expanding,
+isothermal spherical shell surrounding a central galaxy.   
+This model is completly described by three sets ot paremeters that
+define the geometry, kinematics and thermodinamics of the model.
+The geometry is described by the shell's inner radius $R_{in}$ and outer
+radius $R_{out}$, which are related to each other by the expression
+$R_{in} = f_{th}R_{out}$, with $f_{th}=0.9$ as the fiducial value. 
+The temperature of the medium is assumed constant
+and equal to $T=10^4 K$ and it is expanding at a constant velocity
+\vel. This outflow is composed by dust and gas uniformly mixed
+described by the column density \nh and the metallicity $Z$ as
+follows:
 
@@
 
-Where $M_{shell}$ is the mass of the outflow, $m_H$ is the mass of the hydrogen atom and $X_H=0.74$ is the fraction of hydrogen in the cold gas.
+Where $M_{shell}$ is the mass of the outflow, $m_H$ is the mass of the
+hydrogen atom and $X_H=0.74$ is the fraction of hydrogen in the cold
+gas.
 
@@
 
-Where $\langle Z_{cold} \rangle$ is the average metallicity of the cold gas and it is weighted by the product of the mass of cold gas and the \lya luminosity of the disc and bulge $f_Z$. \\
+Where $\langle Z_{cold} \rangle$ is the average metallicity of the
+cold gas and it is weighted by the product of the mass of cold gas and
+the \lya luminosity of the disc and bulge $f_Z$.
 
-We decided to choose this model for two main reasons.
-First, when we analyze observed spectra we can se that the line is spread around the place where line should be when already taking into account the redshift due to the distance to the LAE.
-This implies that the photons before escaping the composed system suffer a change in frequency themselves, which we explain by making them rebound over the inner surface of the shell such as some of them suffer blueshift and other redshift, that even small, is significant and observed.\\
+We decided to choose this model for two main reasons. First, when we
+analyze observed spectra we can se that the line is spread around the
+place where line should be when already taking into account the
+redshift due to the distance to the LAE. This implies that the photons
+before escaping the composed system suffer a change in frequency
+themselves, which we explain by making them rebound over the inner
+surface of the shell such as some of them suffer blueshift and other
+redshift, that even small, is significant and observed.
 
-The second reason is because as the space between the shell and the galaxy is said to be void, the photons that escape from it suffer the scattering process at a far distance from the center, in a way such as if they rebound the chances that it happens in the normal direction to the surface are lower than in any other model.
-This implies that the photons are less likely to re-enter the galaxy so there is no need to start the diffusion inside again, allowing us to divide the spectrum creation process into 2 independent events, saving computational time and simplifying the model to its best.
-\\
+The second reason is because as the space between the shell and the
+galaxy is said to be void, the photons that escape from it suffer the
+scattering process at a far distance from the center, in a way such as
+if they rebound the chances that it happens in the normal direction to
+the surface are lower than in any other model. This implies that the
+photons are less likely to re-enter the galaxy so there is no need to
+start the diffusion inside again, allowing us to divide the spectrum
+creation process into 2 independent events, saving computational time
+and simplifying the model to its best.
 
@@
 
-The joint model consists of combining the two models that were just explained.
-A rotating spherical galaxy is placed at the center with a thin shell outflow surrounding it as seen in Fig.
-\ref{fig:model}.
-What happens is that the photons that escaped the galaxy enter now into the outflow with the same radial direction that they came out with.
-At the end only a fraction of those manage to get out of the outflow and their wavelengths are measured to find the final spectrum.\\
+The joint model consists of combining the two models that were just
+explained. A rotating spherical galaxy is placed at the center with a
+thin shell outflow surrounding it as seen in
+Fig. \ref{fig:model}. What happens is that the photons that escaped
+the galaxy enter now into the outflow with the same radial direction
+that they came out with. At the end only a fraction of those manage to
+get out of the outflow and their wavelengths are measured to find the
+final spectrum.
 
@@
 \end{center}
-\caption{\textbf{Model:} A central rotating galaxy surrounded by an expanding thin shell outflow.\\
+\caption{\textbf{Model:} A central rotating galaxy surrounded by an expanding thin shell outflow.
 \label{fig:model}}
@@
 
-In order to simulate all the possible cases we set some key parameters for the program to vary, and some others fixed which are defined by the characteristics of LAEs. This are chosen as follows.\\
+In order to simulate all the possible cases we set some key parameters
+for the program to vary, and some others fixed which are defined by
+the characteristics of LAEs. This are chosen as follows.
 
@@
 
-For the first stage there are two fixed parameters: the optical depth $\tau = 10^8$ and the galaxy rotation velocity $v_{gal}=100$ \kms.
-For the second stage there is one fixed parameter: the metallicity of the outflow $Z=-4.0$.
-This 3 fixed values are selected because the characteristics of observed LAEs, especially their low mass and their highest star formation rate of all.\\
+For the first stage there are two fixed parameters: the optical depth
+$\tau = 10^8$ and the galaxy rotation velocity $v_{gal}=100$ \kms. For
+the second stage there is one fixed parameter: the metallicity of the
+outflow $Z=-4.0$. This 3 fixed values are selected because the
+characteristics of observed LAEs, especially their low mass and their
+highest star formation rate of all.
 
@@
 
-We have then 3 parameters left that are going to vary along a wide range. These are: the galaxy viewing angle \ang, the hydrogen column density \nh and the outflow expanding velocity \vel. \\
+We have then 3 parameters left that are going to vary along a wide
+range. These are: the galaxy viewing angle \ang, the hydrogen column
+density \nh and the outflow expanding velocity \vel.
 
-\ang covers 3 different angles: $0^\circ$, $45^\circ$ and $90^\circ$.
-\lognh takes 41 different values from 20.0 to 22.5.
-And \vel covers 5 equidistant velocities from 100 \kms to 500 \kms.
-The permutations of these three are analyzed in section \ref{sec:results}.
+\ang covers 3 different angles: $0^\circ$, $45^\circ$ and
+$90^\circ$. \lognh takes 41 different values from 20.0 to 22.5. And
+\vel covers 5 equidistant velocities from 100 \kms to 500 \kms. The
+permutations of these three are analyzed in section
+\ref{sec:results}.
 

### 2015-02-25 RotacionOutFlows/Paper/ms.tex

@@
 
-\shortauthors{Remolina-Gutierrez, Forero-Romero \& Garavito-Camargo}
+\shortauthors{Remolina-Gutierrez et al.}
 
-\author{ Maria Camila Remolina-Gutierrez, Jaime E. Forero-Romero \& Juan N. Garavito-Camargo}
+\author{Maria Camila Remolina-Gutierrez, Jaime E. Forero-Romero \&
+  Juan N. Garavito-Camargo} 
 \affil{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
 No. 18A-10, Edificio Ip, Bogot\'a, Colombia}
+\author{Julian Mej\'ia}
+\affil{Chile}
+\author{Alvaro Orsi}
+\affil{Spain}
 \email{mc.remolina197@uniandes.edu.co}
@@
 
-\keywords{Galaxies: high-redshift, Lyman Alpha Emission, Galaxy Rotation, Galaxy Outflows ....MISSING....}
+\keywords{Galaxies: high-redshift, Lyman Alpha Emission, Galaxy
+  Rotation, Galaxy Outflows ....MISSING....}
 
@@
 
-The outcoming spectra of the rotating galaxy is then affected by a symmetric thin shell of expanding
-gas at a constant velocity following the model proposed by
-\cite{2014arXiv1404.2958V, Orsi12}.
+The outcoming spectra of the rotating galaxy is then affected by a
+symmetric thin shell of expanding gas at a constant velocity following
+the model proposed by \cite{2014arXiv1404.2958V, Orsi12}.
 
-This paper is structured as follows. In \S \ref{sec:theo} we explain in detail the model of rotation
-and outflow that we use as well of our joint model (Rotation \&
-Outflow). In \S \ref{sec:results} we present  the results of our
-model. In \S \ref{sec:discussion} we compare our results with  recent
-observations of LAEs with special attention of those morphologies that
-present features of galaxy rotation and outflows. In the latest
-section we present our  conclutions.
+This paper is structured as follows. In \S \ref{sec:theo} we explain
+in detail the model of rotation and outflow that we use as well of our
+joint model (Rotation \& Outflow). In \S \ref{sec:results} we present
+the results of our model. In \S \ref{sec:discussion} we compare our
+results with  recent observations of LAEs with special attention of
+those morphologies that present features of galaxy rotation and
+outflows. In the latest section we present our  conclusions.
 
-%LAEs are young and far away galaxies with most of its matter composed by Hydrogen atoms, being the rest heavier elements, like Iron, produced by growing stars burning their material.
-Then, this spectral line tells very important information about the galaxy, most of it actually, which creates a motivation to find a way to model the \lya line according to certain free parameters that vary from a galaxy to another and that can be obtained from observations.
-\\
+%LAEs are young and far away galaxies with most of its matter composed
+%by Hydrogen atoms, being the rest heavier elements, like Iron,
+%produced by growing stars burning their material. Then, this spectral
+%line tells very important information about the galaxy, most of it
+%actually, which creates a motivation to find a way to model the \lya
+%line according to certain free parameters that vary from a galaxy to
+%another and that can be obtained from observations. \\
 
-%Our purpose in this paper is then to make a theoretical model, based on radiative transfer simulations, that use MonteCarlo
-%computational methods to emulate how the line profile is going to come out of the galaxy if it is rotating and has a surrounding
-%outflow, both of this phenomena characterized by key parameters that are going to be described further on the paper. \\
+%Our purpose in this paper is then to make a theoretical model, based
+%on radiative transfer simulations, that use MonteCarlo 
+%computational methods to emulate how the line profile is going to
+%come out of the galaxy if it is rotating and has a surrounding 
+%outflow, both of this phenomena characterized by key parameters that
+%are going to be described further on the paper. \\
 
-%As it has been described, the main purpose of this project is to mix a rotating galaxy with an external outflow surrounding it and analyze the resulting spectrum.
-The rotation model for the LAE consists on a sphere with an homogeneous mixture of dust and hydrogen at a constant temperature undergoing a solid-body rotation.
-The spectrum then depends on the maximum velocity of the sphere, the neutral hydrogen optical depths and the viewing angle.
-What happens is that photons are emitted from a central distribution of gas and escape the sphere after a radiative transfer process that ends at the border.\\
+%As it has been described, the main purpose of this project is to mix
+%a rotating galaxy with an external outflow surrounding it and analyze
+%the resulting spectrum. The rotation model for the LAE consists on a
+%sphere with an homogeneous mixture of dust and hydrogen at a constant
+%temperature undergoing a solid-body rotation. The spectrum then
+%depends on the maximum velocity of the sphere, the neutral hydrogen
+%optical depths and the viewing angle. What happens is that photons
+%are emitted from a central distribution of gas and escape the sphere
+%after a radiative transfer process that ends at the border.\\
 
-%In this model, rotation does not induce any spatial anisotropy in the integrated line flux, the escape fraction or the average
-%number of scatterings, which led to the creation of an analytic approximation for the galaxy spectrum. This mathematical expression
-%helps to minimize the computational costs and lets try with several parameters without spending great amounts of time running the code. \\
+%In this model, rotation does not induce any spatial anisotropy in the
+%integrated line flux, the escape fraction or the average 
+%number of scatterings, which led to the creation of an analytic
+%approximation for the galaxy spectrum. This mathematical expression 
+%helps to minimize the computational costs and lets try with several
+%parameters without spending great amounts of time running the
+%code. \\
 
 %After this photons escape the galaxy to empty space, they encounter a thin spherical shell of matter at a certain radius from the
-%center.
-That material is the outflow of the LAE, created mainly by starbursts which composition is characterized with the parameters of Hydrogen column density and metallicity.
-Besides its components, the galactic outflow is also defined by an expanding constant velocity that affects the redshift of the photons.\\
+%center. That material is the outflow of the LAE, created mainly by
+%starbursts which composition is characterized with the parameters of
+%Hydrogen column density and metallicity. Besides its components, the
+%galactic outflow is also defined by an expanding constant velocity
+%that affects the redshift of the photons.\\
 
-%As there is a lot of empty space inside the shell, it acts as a reflector of photons.
-This means, that when one wants to comes out it is most likely to bounce inside the sphere several times before finally escaping.
-However it is not likely that the photon comes back again inside the galaxy, which helps that the first process does not have to be repeated, and both stages can be treated as consecutive, not simultaneous.
-\\
+%As there is a lot of empty space inside the shell, it acts as a
+%reflector of photons. This means, that when one wants to comes out it
+%is most likely to bounce inside the sphere several times before
+%finally escaping. However it is not likely that the photon comes back
+%again inside the galaxy, which helps that the first process does not
+%have to be repeated, and both stages can be treated as consecutive,
+%not simultaneous. \\
 
@@
 
-We use the simplified rotation model developed by \citep{Garavito14} in which a rotating galaxy is modeled as a solid rotating sphere, with a homogeneous mixture of hydrogen and dust.
-Photons can be initially at the center or can be homogeneously distributed inside the sphere.
-The equations governing this solid-body rotation sphere in which the axis of rotation is defined to be align with the $z$-axis are:
+We use the simplified rotation model developed by \citep{Garavito14}
+in which a rotating galaxy is modeled as a solid rotating sphere, with
+a homogeneous mixture of hydrogen and dust. Photons can be initially
+at the center or can be homogeneously distributed inside the
+sphere. The equations governing this solid-body rotation sphere in
+which the axis of rotation is defined to be align with the $z$-axis
+are:
 
@@
 \begin{equation}
-J(x,b,\phi,i)=\frac{\sqrt{\pi}}{\sqrt{24}a\tau_0}\Bigg{(}\frac{(x-x_{\rm b})^2}{1+{\rm cosh}\Big{[}\sqrt{\frac{2\pi^3}{27}}\frac{|(x-x_{\rm b})^3|}{a\tau_0}\Big{]}}\Bigg{)}
+J(x,b,\phi,i)=\frac{\sqrt{\pi}}{\sqrt{24}a\tau_0}\Bigg{(}\frac{(x-x_{\rm
+    b})^2}{1+{\rm cosh}\Big{[}\sqrt{\frac{2\pi^3}{27}}\frac{|(x-x_{\rm
+        b})^3|}{a\tau_0}\Big{]}}\Bigg{)} 
 \end{equation}
@@
 
-We use the outflow model stated in \citep{Orsi12}. 
-In their model the outflow consists of an homogeneous, expanding,
-isothermal spherical shell surrounding a central galaxy.   
-This model is completly described by three sets ot paremeters that
-define the geometry, kinematics and thermodinamics of the model.
-The geometry is described by the shell's inner radius $R_{in}$ and outer
-radius $R_{out}$, which are related to each other by the expression
-$R_{in} = f_{th}R_{out}$, with $f_{th}=0.9$ as the fiducial value. 
-The temperature of the medium is assumed constant
-and equal to $T=10^4 K$ and it is expanding at a constant velocity
-\vel. This outflow is composed by dust and gas uniformly mixed
-described by the column density \nh and the metallicity $Z$ as
-follows:
+We use an outflow model that follows the characteristics put described
+in \citep{Verhamme06} with the code presented in\citep{Orsi12}.  
+The outflow consists of an isothermal, spherical flow expanding at
+constant velocity \vel.  
+The outflow is empty inside the shell's inner radius $R_{in}$ and
+reaches out to an external radius $R_{out}$.
+The relationship between these two radii is parameterized by $R_{in} =
+f_{th}R_{out}$, with $f_{th}=0.9$ as the fiducial value.  
+The temperature of the medium is assumed constant and equal to $T=10^4
+K$ which sets the velocity dispersion of Maxwell-Boltzmann
+distributions to $v_{\rm th}=12.84$\kms.
 
+The gas has an homogeneous Hydrogen number density inside the flow. 
+The total mass inside the shell is parameterized by its column density
 \begin{equation}
 \label{eq:nh}
-n_H = \frac{X_H M_{shell}}{4\pi m_H {R^2}_{out}}
+N_H = \frac{X_H M_{shell}}{4\pi m_H {R^2}_{out}},
 \end{equation}
-
-Where $M_{shell}$ is the mass of the outflow, $m_H$ is the mass of the
+%
+where $M_{shell}$ is the outflow mass, $m_H$ is the mass of the
 hydrogen atom and $X_H=0.74$ is the fraction of hydrogen in the cold
@@
 
+The outflow also includes dust homogeneously mixed with the gas. 
+The dust optical depth $\tau_d$ is parameterized by the metallicity of
+the cold gas $\langle Z_{cold} \rangle$: 
 \begin{equation}
 \label{eq:z}
-Z = f_Z \langle Z_{cold} \rangle
+\tau_{d} ???? \langle Z_{cold} \rangle
 \end{equation}
 
-Where $\langle Z_{cold} \rangle$ is the average metallicity of the
-cold gas and it is weighted by the product of the mass of cold gas and
-the \lya luminosity of the disc and bulge $f_Z$.
+%We choose this model because it h
+%for two main reasons. First, when we
+%analyze observed spectra we can se that the line is spread around the
+%place where line should be when already taking into account the
+%redshift due to the distance to the LAE. This implies that the photons
+%before escaping the composed system suffer a change in frequency
+%themselves, which we explain by making them rebound over the inner
+%surface of the shell such as some of them suffer blueshift and other
+%redshift, that even small, is significant and observed.
 
-We decided to choose this model for two main reasons. First, when we
-analyze observed spectra we can se that the line is spread around the
-place where line should be when already taking into account the
-redshift due to the distance to the LAE. This implies that the photons
-before escaping the composed system suffer a change in frequency
-themselves, which we explain by making them rebound over the inner
-surface of the shell such as some of them suffer blueshift and other
-redshift, that even small, is significant and observed.
-
-The second reason is because as the space between the shell and the
-galaxy is said to be void, the photons that escape from it suffer the
-scattering process at a far distance from the center, in a way such as
-if they rebound the chances that it happens in the normal direction to
-the surface are lower than in any other model. This implies that the
-photons are less likely to re-enter the galaxy so there is no need to
-start the diffusion inside again, allowing us to divide the spectrum
-creation process into 2 independent events, saving computational time
-and simplifying the model to its best.
+%The second reason is because as the space between the shell and the
+%galaxy is said to be void, the photons that escape from it suffer the
+%scattering process at a far distance from the center, in a way such as
+%if they rebound the chances that it happens in the normal direction to
+%the surface are lower than in any other model. This implies that the
+%photons are less likely to re-enter the galaxy so there is no need to
+%start the diffusion inside again, allowing us to divide the spectrum
+%creation process into 2 independent events, saving computational time
+%and simplifying the model to its best.
 

### 2015-02-25 RotacionOutFlows/Paper/ms.tex
intro update

@@
 \cite{PartridgePeebles} predicted a population of galaxies with a strong 
-Lyman Alpha (\lya) emission,  nowadays galaxies who are selected using the \lya 
+Lyman Alpha (\lya) emission,  nowadays galaxies selected using the \lya 
 line are known as Lyman Alpha Emitters (LAEs). Since the first 
@@
   Chonis2013,Finkelstein2013,Ostlin14} with the aim of exploring the
-extragalactic Universe $cite{}$.  Specially at $z>=2$ since it is when
+extragalactic Universe.  Specially at $z>=2$ since it is when
 the  line is redshifted into the optical regime. With the outcoming of
 new and powerfull telescopes such as the James Webb Space Telescope
-new LAEs are going to be discovered.
+new LAEs are going to be discovered with a better resultation and at
+higher redshifts.
 
-A variety of Astrophysical problems can be studied using LAEs;
-clustering \citep{Behrens13} of galaxies at high redshift,
-Interstellar (ISM) and intergalactic (IGM) medium  properties
-\citep{DijkstraKramer} and cosmological reionization for a recent
-review see \cite{review}  among others. This motivates to study in
-detail the processes that model the morphology of the \lya line.
+This observations have a direct impact in studing the reionization epoch
+see \cite{review} fore more details and references in within,
+properties of the interstellar medium (ISM) and the intergalactic medium (IGM)
+\citep{Behrens13} \citep{DijkstraKramer}, constraining star formation 
+rates, understanding galaxy luminosity functions \cite{Max} and
+studying the large scale structure of the Universe. In all of this
+studies is required a understanding the processes 
+that model the morphology and the emission of the \lya line.
 
-To fully understand the observed spectra of LAEs this galaxies must be
-modeled. 
-However the resonant nature of the lines makes this a challenging
-task.  
-Analytical solutions for the outcoming spectra in simple ISM static
+To fully understand the observed spectra of the LAEs this galaxies must be
+modeled. However the resonant nature of the lines makes this a challenging
+task. Analytical solutions for the outcoming spectra in simple ISM static
 geometries have been derived \cite{Adams72, Harrington73, Neufeld90,
@@
 Line, special attention have been devoted to model the presence   of
-outflows in the galaxy. here different models have attempt to (name
-the models, shell cavities etc.) 
-\citep{Behrens2014}. 
-Most recently \cite{Garavito14} have studied in detail the effect 
-of rotation on the lyman alpha line.
+outflows in the galaxy. Here different models have attempt to 
+simulate more realistic situations involving shlle models, cavities and-- 
+\citep{Behrens2014}. Most recently \cite{Garavito14} have studied in 
+detail the effect of rotation on the lyman alpha line.
 

### 2015-02-25 RotacionOutFlows/Paper/ms.tex
Max cite and reordering paragraphs

@@
 geometries have been derived \cite{Adams72, Harrington73, Neufeld90,
-  Dijkstra06}. Recent hydrodynamical simulations have studied the
+  Dijkstra06}.Most recently \cite{Garavito14} have studied in
+detail the effect of rotation on the lyman alpha line.
+Hydrodynamical simulations have studied the
 outcomming spectra of LAEs in large scale simulations, while some
@@
 used in order to understand the effect of the gas kinematics in the
-Line, special attention have been devoted to model the presence   of
-outflows in the galaxy. Here different models have attempt to 
-simulate more realistic situations involving shlle models, cavities and-- 
-\citep{Behrens2014}. Most recently \cite{Garavito14} have studied in 
-detail the effect of rotation on the lyman alpha line.
+\lya line.
 
-As many previous studies have shown outflows are present in LAEs
-(\textbf{References}), the outflows are mainly a consecuence of the
+Especial attention have been devoted to model the presence of
+outflows in the galaxy, motivates by previous observational 
+studies . Outflows are a consecuence of the
 intergalactic medium (IGM) being ejected from the galaxy due to
-supernova explotions. 
-However rotation should also be present in this galaxies. The joint
-effect of the two above properties should have a direct effect on the
-morphology of the \lya line.
+supernova explotions. Here different models have attempt to 
+simulate more realistic situations involving shell models and cavities. 
+\citep{Behrens2014}.
 
-This effect is the motivation of this paper in which we combine the
-effect of rotation  follow by an outflow. We proposed a simplyfied
-model in which the galaxy is modeled as an sphere, with an homogeneous
-mixture of dust and hydrogen at a constant temperature and undergoing
-solid-body rotation.
+Despite the fact that outflows have been broadly studied 
+rotation should also be present in this galaxies. T
+he joint effect of the two above properties should have 
+a direct effect on the morphology of the \lya line.
+
+Study this effect is the main motivation of this paper in which we combine the
+effect of rotation followed by an outflow. We proposed a simplyfied
+model in which the galaxy is modeled as an sphere undergoing
+solid-body rotation, with an homogeneous mixture of dust and 
+hydrogen at a constant temperature.
 

### 2015-03-06 Paper/ms.tex
Organizing Everything + English Names

--- 2015-02-25 RotacionOutFlows/Paper/ms.tex
@@
 observed LAE by \cite{DjorgovskiThompson} different teams have 
-observed several LAEs \cite{Kulas12, Yamada2012,
-  Chonis2013,Finkelstein2013,Ostlin14} with the aim of exploring the
-extragalactic Universe.  Specially at $z>=2$ since it is when
+observed several LAEs \cite{Rhoads00,Gawiser2007,Koehler2007,Ouchi08,Yamada2012,Schenker2012,Kulas12, Yamada2012, Chonis2013,Finkelstein2013,Ostlin14} 
+with the aim of exploring the extragalactic Universe.  Specially at $z>=2$ since it is when
 the  line is redshifted into the optical regime. With the outcoming of
-new and powerfull telescopes such as the James Webb Space Telescope
-new LAEs are going to be discovered with a better resultation and at
+new and powerful telescopes such as the James Webb Space Telescope
+new LAEs are going to be discovered with a better resolution and at
 higher redshifts.
 
-This observations have a direct impact in studing the reionization epoch
+This observations have a direct impact in studying the reionization epoch
 see \cite{review} fore more details and references in within,
@@
 \citep{Behrens13} \citep{DijkstraKramer}, constraining star formation 
-rates, understanding galaxy luminosity functions \cite{Max} and
+rates of high redshift galaxies, understanding galaxy luminosity functions \cite{Max} and
 studying the large scale structure of the Universe. In all of this
-studies is required a understanding the processes 
-that model the morphology and the emission of the \lya line.
+studies is required an understanding of the processes 
+that model the morphology and the radiate transfer process 
+behind  of the \lya line.
 
 To fully understand the observed spectra of the LAEs this galaxies must be
-modeled. However the resonant nature of the lines makes this a challenging
+modeled. However the resonant nature of the line makes this a challenging
 task. Analytical solutions for the outcoming spectra in simple ISM static
 geometries have been derived \cite{Adams72, Harrington73, Neufeld90,
-  Dijkstra06}.Most recently \cite{Garavito14} have studied in
+  Dijkstra06}. Radiative transfer codes \citep{DijkstraKramer, Laursen09, Verhamme06, CLARA}
+have been developed in order to understand the effect of the gas kinematics in the
+\lya line, special attention have been devoted to  the effects of clumpy media \citep{Hansen06} and
+expanding/contracting shell/spherical geometries started to be studied
+\citep{Ahn03,Verhamme06,Dijkstra06}. Recently \cite{Garavito14} have studied in
 detail the effect of rotation on the lyman alpha line.
-Hydrodynamical simulations have studied the
-outcomming spectra of LAEs in large scale simulations, while some
-others have studied detailed galaxies \citep{Verhamme12}.  
-Radiative transfer codes \citep{Laursen09, Verhamme06, CLARA}have been
-used in order to understand the effect of the gas kinematics in the
-\lya line.
+Hydrodynamic simulations have studied the
+outcomming spectra of LAEs in large scale simulations \cite{Forero12},  
+Recently Monte Carlo codes have been used in 
+hydrodynamic simulations to study in detail individual galaxies 
+\citep{Laursen09,Barnes11,Verhamme12,Yajima12}.
 
@@
 outflows in the galaxy, motivates by previous observational 
-studies . Outflows are a consecuence of the
-intergalactic medium (IGM) being ejected from the galaxy due to
-supernova explotions. Here different models have attempt to 
+studies*. Outflows are a consequence of the
+interstellar medium (ISM) being ejected from the galaxy due to
+supernova explosions. Here different models have attempt to 
 simulate more realistic situations involving shell models and cavities. 
@@
 Despite the fact that outflows have been broadly studied 
-rotation should also be present in this galaxies. T
-he joint effect of the two above properties should have 
+rotation should also be present in this galaxies. The joint 
+effect of the two above properties should have 
 a direct effect on the morphology of the \lya line.
@@
 Study this effect is the main motivation of this paper in which we combine the
-effect of rotation followed by an outflow. We proposed a simplyfied
+effect of rotation followed by an outflow. We proposed a simplified
 model in which the galaxy is modeled as an sphere undergoing
@@
 This paper is structured as follows. In \S \ref{sec:theo} we explain
-in detail the model of rotation and outflow that we use as well of our
+in detail the model of rotation and outflow that we use as well and our
 joint model (Rotation \& Outflow). In \S \ref{sec:results} we present

### 2015-03-06 AnalyticSpectra/analytic_solution.c
dynamic range in x for the analytic solution

@@ -2,7 +2,7 @@
 #include <math.h>
 #include <stdlib.h>
 #define NPOINTS 1000
-#define NPOINTSX 100
+#define NPOINTSX 400
 #define TEMP 10000.0
 #define R 1.0
 #define PI 3.141592653589793238462643383279502884197169
@@ -13,12 +13,17 @@
   transfer problem of a rotating sphere.
 
   The solution was computed by Mark Dijsktra and is published in the 
-  paper: Garavito-Camargo, Forero-Romero, Dijkstra, ApJ ....
+  paper: 
+
+  The Impact of Gas Bulk Rotation on the Lyalpha Line
+  Garavito-Camargo, Forero-Romero, Dijkstra, 
+  The Astrophysical Journal, Volume 795, Issue 2, article id. 120, 12 pp. (2014)
 
   Author: Jaime E. Forero-Romero (Uniandes)
-  Creation date: 14-Jun-2014
+  Creation date: 14-Jun-2014. 
 
   Modifications:
+  6-Mar-2015. Included dynamic range in x.
 */
 
 double J_surface(double x, double b, double phi, double i_angle, double tau0, double v_rot);
@@ -26,13 +31,13 @@ int main(int argc, char **argv){
   int i, j, k;
   double *x;
   double *j_int;
-  double min_x=-50.0;
-  double max_x= 50.0;
-  double delta_x = (max_x-min_x)/NPOINTSX;
+  double delta_x;
   double delta_phi = 2.0*PI/NPOINTS;
   double delta_b = 0.9999/NPOINTS;
   double tau, v_rot, i_angle;
   double b, phi;
+  double min_x;
+  double max_x;
 
   if(argc!=4){
     fprintf(stderr, "USAGE: %s\n", USAGE);
@@ -45,6 +50,11 @@ int main(int argc, char **argv){
   i_angle = i_angle*PI/180.0;
   
   fprintf(stderr, "%f %f %f\n", tau, v_rot, i_angle);
+
+
+  min_x = -(pow(10,(log10(tau))/2.5) + v_rot)/15.0;
+  max_x = (pow(10,(log10(tau))/2.5) + v_rot)/15.0;
+  delta_x = (max_x-min_x)/NPOINTSX;
 
   if(!(x=malloc(sizeof(double)*NPOINTSX))){
     fprintf(stderr, "Problem with memory allocation");
[…]

### 2015-03-07 Simulation/SpectraVisualization.Rmd
plots

---
title: "Simulation Plots"
author: "Maria Camila Remolina-Gutierrez"
output: html_document
runtime: shiny
---

## Galaxy + Outflow Spectra

```{r, echo=FALSE}

inputPanel(
  sliderInput("v_galaxy", label = "Galaxy Velocity:",
              min = 1, max = 4, value = 1, step = 1),

  sliderInput("v_outflow", label = "Outflow Velocity:",
              min = 100, max = 500, value = 100, step = 100),

  sliderInput("lognh_outflow", label = "Outflow Column Density:",
              min = 1, max = 41, value = 1, step = 1)
)

renderPlot({

  library(ggplot2)

  v_galaxy_options <- c(0, 20, 100, 200)

  lognh_options <- c(20.0, 20.0625, 20.125, 20.1875, 20.25, 20.3125, 20.375, 20.4375, 20.5, 20.5625, 20.625, 20.6875, 20.75, 20.8125, 20.875, 20.9375, 21.0, 21.0625, 21.125, 21.1875, 21.25, 21.3125, 21.375, 21.4375, 21.5, 21.5625, 21.625, 21.6875, 21.75, 21.8125, 21.875, 21.9375, 22.0, 22.0625, 22.125, 22.1875, 22.25, 22.3125, 22.375, 22.4375, 22.5)

  spectrum <- read.csv("./data/galaxyoutflow.csv")

  vg <- v_galaxy_options[input$v_galaxy]
  vo <- input$v_outflow
  lnh <- lognh_options[input$lognh_outflow]

  spectrum_sub <- spectrum[spectrum$v_gal==vg,]
  spectrum_sub <- spectrum_sub[spectrum_sub$v_out==vo,]
  spectrum_sub <- spectrum_sub[spectrum_sub$lognh==lnh,]

  text = paste(c("v_out =", vo, "km/s \n log(nH) =", lnh, "\n v_gal =", vg, "km/s\n"), collapse=" ")

  ggplot(spectrum_sub, aes(x=x,y=y)) + geom_line(col = 30, lw = 2) + labs(title=text, x="Lambda (A)", y="Intensity (Arbitrary Units)") + xlim(1210, 1232) + ylim(0, 7100) + theme(plot.title = element_text(hjust = 1, vjust = 1))

  })
```

### 2015-03-18 Paper/ms.tex
fixing galaxy parameters

@@
 
+\subsubsection{Galaxy Parameters}
+
+Our aim is to provide a realistic baseline to compare against
+observations of LAES at $z\sim 3$. 
+It has been found by analysis of the abundance and angular correlation
+function that LAES reside in DM halos of masses in the range
+$10^{10}-10^{11}$\Msun \cite{WalkerSoler2012}. 
+This mass range corresponds to maximum circular velocities in the
+range $60-125$\kms and a median halo scale radius of
+$15$kpc. Considering that these galaxies are gas dominated we
+approximate their neutral hydrogen gas contents has half their total
+baryonic content estimated from the cosmological baryon to dark matter
+abundances $\Omega_b/\Omega_{dm}=0.1825$ \citep{Planck2015}, which
+gives us gaseous masses in the range $10^{9}-10^{10}$\Msun.
+
+\footnote{These results were found using the N-body data
+  available in \url{www.cosmosim.org}}.
+
+From these constraints we chose to model our galaxies as sphere of
+radius $15$kpc and rotation velocities in the range
+$60-125$\kms.
+
 \subsubsection{Fixed Parameters}

### 2015-03-18 AnalyticSpectra/estimates.py
mini script to estimate the values for the central galaxy models

@@ -1,0 +1,17 @@
+from math import *
+M_halo =1E10
+H_fraction = 0.2
+gas_fraction = 0.75
+cosmic_fraction = 0.18
+M = M_halo * cosmic_fraction * gas_fraction * H_fraction
+m_H=1.6E-27
+M_sun_in_kg = 1.9E30
+radius = 15000
+pc_to_m = 3.8E16
+m_to_cm = 100
+n_H = (M * M_sun_in_kg/m_H)/((4.0*pi/3.0)*(radius*pc_to_m*m_to_cm)**3)
+sigma = 1.0E-14
+print "gas mass", M/1.0E8
+print "number density", n_H
+tau = n_H * radius * pc_to_m * m_to_cm * sigma 
+print "optical depth", tau

### 2015-03-18 Paper/ms.tex
finished central galaxy model section

@@
 range $60-125$\kms and a median halo scale radius of
-$15$kpc. Considering that these galaxies are gas dominated we
-approximate their neutral hydrogen gas contents has half their total
-baryonic content estimated from the cosmological baryon to dark matter
-abundances $\Omega_b/\Omega_{dm}=0.1825$ \citep{Planck2015}, which
-gives us gaseous masses in the range $10^{9}-10^{10}$\Msun.
+$15$kpc.  \footnote{These results were
+  found using the  N-body data available in \url{www.cosmosim.org}}.
 
-\footnote{These results were found using the N-body data
-  available in \url{www.cosmosim.org}}.
+These galaxies have gas fractions close to $20\%$
+\citep{Narayanan2012}. We approximate that the hydrogen content is
+$20\%$ the total baryonic content from the cosmological baryon to dark
+matter  abundances $\Omega_b/\Omega_{dm}=0.1825$ \citep{Planck2015},
+multiplied by a primordial Hydrogen fraction of $0.75$.
+All these considerations gives us hydrogen masses in the range
+$2.7\times 10^{8}-2.7\times 10^{9}$\Msun.
 
-From these constraints we chose to model our galaxies as sphere of
-radius $15$kpc and rotation velocities in the range
-$60-125$\kms.
+These choices give us a range for the number density of Hydrogen atoms
+of $4\times10^{-4}-4\times 10^{-3}$ atoms cm$^{-3}$. 
+With a Lyman-$\alpha$ cross section at the line center of
+$\sigma_{H}=1.0\times 10^{-14}$ cm$^{2}$ we finally obtain that the
+optical depth from the cloud's center  should be in the range $\tau=2
+\times 10^{5} - 2 \times 10^{6}$.
+
+From these constraints we chose to model two kinds of central galaxies
+in the extremes of these distributions. The first has $\tau =2\times
+10^5$ and a raotational velocity of $60$\kms. The second has
+$\tau=2\times 10^6$ and a rotational velocity of $125$\kms.
 

### 2015-03-18 Paper/ms.tex
updates in paper

@@
 
-\cite{PartridgePeebles} predicted a population of galaxies with a strong 
-Lyman Alpha (\lya) emission,  nowadays galaxies selected using the \lya 
-line are known as Lyman Alpha Emitters (LAEs). Since the first 
-observed LAE by \cite{DjorgovskiThompson} different teams have 
-observed several LAEs \cite{Rhoads00,Gawiser2007,Koehler2007,Ouchi08,Yamada2012,Schenker2012,Kulas12, Yamada2012, Chonis2013,Finkelstein2013,Ostlin14} 
-with the aim of exploring the extragalactic Universe.  Specially at $z>=2$ since it is when
-the  line is redshifted into the optical regime. With the outcoming of
-new and powerful telescopes such as the James Webb Space Telescope
-new LAEs are going to be discovered with a better resolution and at
+\cite{PartridgePeebles} predicted a population of galaxies with a strong Lyman Alpha (\lya) emission,  nowadays galaxies selected using the \lya line are known as Lyman Alpha Emitters (LAEs).
+Since the first observed LAE by \cite{DjorgovskiThompson} different teams have observed several LAEs \cite{Rhoads00,Gawiser2007,Koehler2007,Ouchi08,Yamada2012,Schenker2012,Kulas12, Yamada2012, Chonis2013,Finkelstein2013,Ostlin14} with the aim of exploring the extragalactic Universe.
+Specially at $z>=2$ since it is when the  line is redshifted into the optical regime.
+With the outcoming of new and powerful telescopes such as the James Webb Space Telescope new LAEs are going to be discovered with a better resolution and at
 higher redshifts.
 
-This observations have a direct impact in studying the reionization epoch
-see \cite{review} fore more details and references in within,
-properties of the interstellar medium (ISM) and the intergalactic medium (IGM)
-\citep{Behrens13} \citep{DijkstraKramer}, constraining star formation 
-rates of high redshift galaxies, understanding galaxy luminosity functions \cite{Max} and
-studying the large scale structure of the Universe. In all of this
-studies is required an understanding of the processes 
-that model the morphology and the radiate transfer process 
+This observations have a direct impact in studying the reionization epoch see \cite{review} fore more details and references in within, properties of the interstellar medium (ISM) and the intergalactic medium (IGM) \citep{Behrens13} \citep{DijkstraKramer}, constraining star formation rates of high redshift galaxies, understanding galaxy luminosity functions \cite{Max} and studying the large scale structure of the Universe.
+In all of this
+studies is required an understanding of the processes that model the morphology and the radiate transfer process 
 behind  of the \lya line.
 
-To fully understand the observed spectra of the LAEs this galaxies must be
-modeled. However the resonant nature of the line makes this a challenging
-task. Analytical solutions for the outcoming spectra in simple ISM static
-geometries have been derived \cite{Adams72, Harrington73, Neufeld90,
-  Dijkstra06}. Radiative transfer codes \citep{DijkstraKramer, Laursen09, Verhamme06, CLARA}
-have been developed in order to understand the effect of the gas kinematics in the
-\lya line, special attention have been devoted to  the effects of clumpy media \citep{Hansen06} and
-expanding/contracting shell/spherical geometries started to be studied
-\citep{Ahn03,Verhamme06,Dijkstra06}. Recently \cite{Garavito14} have studied in
-detail the effect of rotation on the lyman alpha line.
-Hydrodynamic simulations have studied the
-outcomming spectra of LAEs in large scale simulations \cite{Forero12},  
-Recently Monte Carlo codes have been used in 
-hydrodynamic simulations to study in detail individual galaxies 
-\citep{Laursen09,Barnes11,Verhamme12,Yajima12}.
+To fully understand the observed spectra of the LAEs this galaxies must be modeled.
+However the resonant nature of the line makes this a challenging task.
+Analytical solutions for the outcoming spectra in simple ISM static
+geometries have been derived \cite{Adams72, Harrington73, Neufeld90, Dijkstra06}.
+Radiative transfer codes \citep{DijkstraKramer, Laursen09, Verhamme06, CLARA} have been developed in order to understand the effect of the gas kinematics in the \lya line, special attention have been devoted to  the effects of clumpy media \citep{Hansen06} and expanding/contracting shell/spherical geometries started to be studied \citep{Ahn03,Verhamme06,Dijkstra06}.
+Recently \cite{Garavito14} have studied in detail the effect of rotation on the lyman alpha line.Hydrodynamic simulations have studied the outcomming spectra of LAEs in large scale simulations \cite{Forero12}.
+Recently Monte Carlo codes have been used in hydrodynamic simulations to study in detail individual galaxies \citep{Laursen09,Barnes11,Verhamme12,Yajima12}.
 
-Especial attention have been devoted to model the presence of
-outflows in the galaxy, motivates by previous observational 
-studies*. Outflows are a consequence of the
-interstellar medium (ISM) being ejected from the galaxy due to
-supernova explosions. Here different models have attempt to 
-simulate more realistic situations involving shell models and cavities. 
+Especial attention have been devoted to model the presence of outflows in the galaxy, motivates by previous observational studies*.
+Outflows are a consequence of the interstellar medium (ISM) being ejected from the galaxy due to supernova explosions.
+Here different models have attempt to simulate more realistic situations involving shell models and cavities.
 \citep{Behrens2014}.
 
-Despite the fact that outflows have been broadly studied 
-rotation should also be present in this galaxies. The joint 
-effect of the two above properties should have 
-a direct effect on the morphology of the \lya line.
+Despite the fact that outflows have been broadly studied rotation should also be present in this galaxies. The joint 
+effect of the two above properties should have a direct effect on the morphology of the \lya line.
 
-Study this effect is the main motivation of this paper in which we combine the
-effect of rotation followed by an outflow. We proposed a simplified
-model in which the galaxy is modeled as an sphere undergoing
-solid-body rotation, with an homogeneous mixture of dust and 
-hydrogen at a constant temperature.
+Study this effect is the main motivation of this paper in which we combine the effect of rotation followed by an outflow.
+We proposed a simplified model in which the galaxy is modeled as an sphere undergoing solid-body rotation, with an homogeneous mixture of dust and hydrogen at a constant temperature.
 
-The solid-body rotation does not induce any spatial anisotropy in the
-integrated line flux,  the escape fraction or in the average number of
-scatterings. This symmetry allows to the creation of an analytic
-approximation for the galaxy spectrum  proposed, see \cite{Garavito14}
-for details. In this model the optical depth $\tau_{H}$, the  rotation
-velocity $V_{max}$ and the inclination angle $\theta$ are free
-parameters.
+The solid-body rotation does not induce any spatial anisotropy in the integrated line flux,  the escape fraction or in the average number of scatterings.
+This symmetry allows to the creation of an analytic approximation for the galaxy spectrum  proposed, see \cite{Garavito14} for details.
+In this model the optical depth $\tau_{H}$, the  rotation velocity $V_{max}$ and the inclination angle $\theta$ are free parameters.
 
-The outcoming spectra of the rotating galaxy is then affected by a
-symmetric thin shell of expanding gas at a constant velocity following
-the model proposed by \cite{2014arXiv1404.2958V, Orsi12}.
+The outcoming spectra of the rotating galaxy is then affected by a symmetric thin shell of expanding gas at a constant velocity following the model proposed by \cite{2014arXiv1404.2958V, Orsi12}.
 
-This paper is structured as follows. In \S \ref{sec:theo} we explain
-in detail the model of rotation and outflow that we use as well and our
-joint model (Rotation \& Outflow). In \S \ref{sec:results} we present
-the results of our model. In \S \ref{sec:discussion} we compare our
-results with recent observations of LAEs with special attention of
-those morphologies that present features of galaxy rotation and
-outflows. In the latest section we present our conclusions.
+This paper is structured as follows.
+In \S \ref{sec:theo} we explain in detail the model of rotation and outflow that we use as well and our joint model (Rotation \& Outflow).
+In \S \ref{sec:results} we present the results of our model.
+In \S \ref{sec:discussion} we compare our results with recent observations of LAEs with special attention of
+those morphologies that present features of galaxy rotation and outflows. In the latest section we present our conclusions.
 
@@
 \label{sec:theo}
-In this section we describe the two different models that together are
-used to reproduce a real and consistent \lya profile. The first one is
-a rotation model for the galaxy and the second is a thin shell model
-for the outflow. \\
+In this section we describe the two different models that together are used to reproduce a real and consistent \lya profile.
+The first one is a rotation model for the galaxy and the second is a thin shell model for the outflow.
+\\
 
@@
 
-We use the simplified rotation model developed by \citep{Garavito14}
-in which a rotating galaxy is modeled as a solid rotating sphere, with
-a homogeneous mixture of hydrogen and dust. Photons can be initially
-at the center or can be homogeneously distributed inside the
-sphere. The equations governing this solid-body rotation sphere in
-which the axis of rotation is defined to be align with the $z$-axis
-are:
+We use the simplified rotation model developed by \citep{Garavito14} in which a rotating galaxy is modeled as a solid rotating sphere, with a homogeneous mixture of hydrogen and dust.
+Photons can be initially at the center or can be homogeneously distributed inside the sphere.
+The equations governing this solid-body rotation sphere in
+which the axis of rotation is defined to be align with the $z$-axis are:
 
@@
 
-Where $R$ is the radius of the sphere and $V_{\rm max}$ is the linear
-velocity at the sphere's surface. The minus/plus sign in the
-$x$/$y$-component of the velocity indicates the direction of
-rotation. In this case we take the angular velocity in the same
-direction as the $\hat{k}$ unit vector.
+Where $R$ is the radius of the sphere and $V_{\rm max}$ is the linear velocity at the sphere's surface.
+The minus/plus sign in the $x$/$y$-component of the velocity indicates the direction of rotation.
+In this case we take the angular velocity in the same direction as the $\hat{k}$ unit vector.
 
-In this work we use the analytical expression for rotation derived in
-\citep{Garavito14} where a rotating sphere can be seen as a static
-sphere in the laboratory frame with a bulk velocity difference in each
-surface element with respect 
-to a distant observer. 
+In this work we use the analytical expression for rotation derived in \citep{Garavito14} where a rotating sphere can be seen as a static sphere in the laboratory frame with a bulk velocity difference in each surface element with respect to a distant observer.
 With the previous analysis the outcoming spectra can be expressed as:
@@
 
-Where $J(x, b, \phi, i)$ is the spectrum of the flux emerging from the
-surface at point $(b, \phi)$ and is expressed as:
+Where $J(x, b, \phi, i)$ is the spectrum of the flux emerging from the surface at point $(b, \phi)$ and is expressed as:
 
@@
 
-We use an outflow model that follows the characteristics put described
-in \citep{Verhamme06} with the code presented in\citep{Orsi12}.  
+We use an outflow model that follows the characteristics put described in \citep{Verhamme06} with the code presented in\citep{Orsi12}.
 The outflow consists of an isothermal, spherical flow expanding at
-constant velocity \vel.  
-The outflow is empty inside the shell's inner radius $R_{in}$ and
-reaches out to an external radius $R_{out}$.
-The relationship between these two radii is parameterized by $R_{in} =
+constant velocity \vel.  The outflow is empty inside the shell's inner radius $R_{in}$ and
+reaches out to an external radius $R_{out}$. The relationship between these two radii is parameterized by $R_{in} =
 f_{th}R_{out}$, with $f_{th}=0.9$ as the fiducial value.
-The temperature of the medium is assumed constant and equal to $T=10^4
-K$ which sets the velocity dispersion of Maxwell-Boltzmann
-distributions to $v_{\rm th}=12.84$\kms.
+The temperature of the medium is assumed constant and equal to $T=10^4 K$ which sets the velocity dispersion of Maxwell-Boltzmann distributions to $v_{\rm th}=12.84$\kms.
 
-The gas has an homogeneous Hydrogen number density inside the flow. 
-The total mass inside the shell is parameterized by its column density
+The gas has an homogeneous Hydrogen number density inside the flow. The total mass inside the shell is parameterized by its column density
+
 \begin{equation}
@@
 %
-where $M_{shell}$ is the outflow mass, $m_H$ is the mass of the
-hydrogen atom and $X_H=0.74$ is the fraction of hydrogen in the cold
-gas.
+where $M_{shell}$ is the outflow mass, $m_H$ is the mass of the hydrogen atom and $X_H=0.74$ is the fraction of hydrogen in the cold gas.
 
-The outflow also includes dust homogeneously mixed with the gas. 
-The dust optical depth $\tau_d$ is parameterized by the metallicity of
-the cold gas $\langle Z_{cold} \rangle$: 
+The outflow also includes dust homogeneously mixed with the gas. The dust optical depth $\tau_d$ is parameterized by the metallicity of the cold gas $\langle Z_{cold} \rangle$: 
 \begin{equation}
@@
 
-The joint model consists of combining the two models that were just
-explained. A rotating spherical galaxy is placed at the center with a
-thin shell outflow surrounding it as seen in
-Fig. \ref{fig:model}. What happens is that the photons that escaped
-the galaxy enter now into the outflow with the same radial direction
-that they came out with. At the end only a fraction of those manage to
-get out of the outflow and their wavelengths are measured to find the
+The joint model consists of combining the two models that were just explained.
+A rotating spherical galaxy is placed at the center with a thin shell outflow surrounding it as seen in Fig.
+\ref{fig:model}.
+What happens is that the photons that escaped the galaxy enter now into the outflow with the same radial direction that they came out with.
+At the end only a fraction of those manage to get out of the outflow and their wavelengths are measured to find the
 final spectrum.
@@
 
-In order to simulate all the possible cases we set some key parameters
-for the program to vary, and some others fixed which are defined by
-the characteristics of LAEs. This are chosen as follows.
+In order to simulate all the possible cases we set some key parameters for the program to vary, and some others fixed which are defined by the characteristics of LAEs. This are chosen as follows.
 
@@
 
-Our aim is to provide a realistic baseline to compare against
-observations of LAES at $z\sim 3$. 
-It has been found by analysis of the abundance and angular correlation
-function that LAES reside in DM halos of masses in the range
-$10^{10}-10^{11}$\Msun \cite{WalkerSoler2012}. 
-This mass range corresponds to maximum circular velocities in the
-range $60-125$\kms and a median halo scale radius of
-$15$kpc.  \footnote{These results were
-  found using the  N-body data available in \url{www.cosmosim.org}}.
+Our aim is to provide a realistic baseline to compare against observations of LAES at $z\sim 3$.
+It has been found by analysis of the abundance and angular correlation function that LAES reside in DM halos of masses in the range
+$10^{10}-10^{11}$\Msun \cite{WalkerSoler2012}. This mass range corresponds to maximum circular velocities in the
+range $60-125$\kms and a median halo scale radius of $15$kpc.  \footnote{These results were found using the  N-body data available in \url{www.cosmosim.org}}.
 
-These galaxies have gas fractions close to $20\%$
-\citep{Narayanan2012}. We approximate that the hydrogen content is
-$20\%$ the total baryonic content from the cosmological baryon to dark
-matter  abundances $\Omega_b/\Omega_{dm}=0.1825$ \citep{Planck2015},
-multiplied by a primordial Hydrogen fraction of $0.75$.
-All these considerations gives us hydrogen masses in the range
-$2.7\times 10^{8}-2.7\times 10^{9}$\Msun.
+These galaxies have gas fractions close to $20\%$ \citep{Narayanan2012}. We approximate that the hydrogen content is
+$20\%$ the total baryonic content from the cosmological baryon to dark matter  abundances $\Omega_b/\Omega_{dm}=0.1825$ \citep{Planck2015}, multiplied by a primordial Hydrogen fraction of $0.75$.
+All these considerations gives us hydrogen masses in the range $2.7\times 10^{8}-2.7\times 10^{9}$\Msun.
 
-These choices give us a range for the number density of Hydrogen atoms
-of $4\times10^{-4}-4\times 10^{-3}$ atoms cm$^{-3}$. 
-With a Lyman-$\alpha$ cross section at the line center of
-$\sigma_{H}=1.0\times 10^{-14}$ cm$^{2}$ we finally obtain that the
-optical depth from the cloud's center  should be in the range $\tau=2
-\times 10^{5} - 2 \times 10^{6}$.
+These choices give us a range for the number density of Hydrogen atoms of $4\times10^{-4}-4\times 10^{-3}$ atoms cm$^{-3}$.
+With a Lyman-$\alpha$ cross section at the line center of $\sigma_{H}=1.0\times 10^{-14}$ cm$^{2}$ we finally obtain that the optical depth from the cloud's center  should be in the range $\tau=2 \times 10^{5} - 2 \times 10^{6}$.
 
-From these constraints we chose to model two kinds of central galaxies
-in the extremes of these distributions. The first has $\tau =2\times
-10^5$ and a raotational velocity of $60$\kms. The second has
-$\tau=2\times 10^6$ and a rotational velocity of $125$\kms.
+From these constraints we chose to model two kinds of central galaxies in the extremes of these distributions.
+The first has $\tau =2\times 10^5$ and a raotational velocity of $60$\kms.
+The second has $\tau=2\times 10^6$ and a rotational velocity of $125$\kms.
 
-\subsubsection{Fixed Parameters}
-
-For the first stage there are two fixed parameters: the optical depth
-$\tau = 10^8$ and the galaxy rotation velocity $v_{gal}=100$ \kms. For
-the second stage there is one fixed parameter: the metallicity of the
-outflow $Z=-4.0$. This 3 fixed values are selected because the
-characteristics of observed LAEs, especially their low mass and their
+For the first stage there are two fixed parameters: the optical depth $\tau = 10^8$ and the galaxy viewing angle \ang = $90^\circ$.
+For the second stage there is one fixed parameter: the metallicity of the outflow $Z=-4.0$.
+This 3 fixed values are selected because the characteristics of observed LAEs, especially their low mass and their
 highest star formation rate of all.
 
-\subsubsection{Free Parameters}
+We have then 3 parameters left that are going to vary along a wide range.
+These are: the galaxy rotation velocity \vgal, the outflow hydrogen column density \nh and the outflow expanding velocity \vout.
 
-We have then 3 parameters left that are going to vary along a wide
-range. These are: the galaxy viewing angle \ang, the hydrogen column
-density \nh and the outflow expanding velocity \vel.
-
-\ang covers 3 different angles: $0^\circ$, $45^\circ$ and
-$90^\circ$. \lognh takes 41 different values from 20.0 to 22.5. And
-\vel covers 5 equidistant velocities from 100 \kms to 500 \kms. The
-permutations of these three are analyzed in section
-\ref{sec:results}.
-
-\section{Results}
-\label{sec:results}
+\vgal covers 3 different angles: $20$ \kms, $100$ \kms and $200$ \kms.
+\lognh takes 41 different values from $20.0$ to $22.5$.
+And \vout covers 5 equidistant velocities from $100$ \kms to $500$ \kms.
+The permutations of these three are analyzed in section \ref{sec:results}.
 
@@
 
-\subsection{Influences of the Free Parameters}
-
 In order to study the influence of each of the three free parameters, we fix two of them and see how the final spectrum varies along the other one left. In each case we will state these changes.
 
-\subsubsection{Influence of the Galaxy Viewing Angle: \ang}
+\subsection{Influence of the Galaxy Rotation Velocity: \vgal}
 
-If one sets fixed outflow \vel and \lognh in each case the viewing angle has the same effect: it increases proportionally the intensity.
+If one sets fixed outflow \vout and \lognh in each case the rotation velocity has the same effect: it increases proportionally the intensities.
 However this change is not that significant.
@@
 Fig.
-\ref{fig:influence_ang} helps visualize this effect in a better way.
+\ref{fig:influence_vgal} helps visualize this effect in a better way.
 
@@
 \begin{center}
-  \includegraphics[width=0.5\textwidth]{./figures/influence_ang.png}
+  \includegraphics[width=0.5\textwidth]{./figures/inf_vgal_soft.png}
 \end{center}
-\caption{\textbf{Influence of Galaxy Viewing Angle:} The values of the fixed parameters are \vel = 100 \kms and \lognh = 21.3125.
-The 3 possible angles are shown in the plot with different colors.
+\caption{\textbf{Influence of Galaxy Rotation Velocity:} The values of the fixed parameters are \vout = $100$ \kms and \lognh = $20.9375$.
+The 3 possible velocities are shown in the plot with different line styles.
 The increase is visible as well as its small enlargement factor.\\
-\label{fig:influence_ang}}
+\label{fig:influence_vgal}}
 \end{figure}
 
-\subsubsection{Influence of the Outflow Hydrogen Column Density: \lognh }
+\subsection{Influence of the Outflow Hydrogen Column Density: \lognh }
 
 The effect of the \lognh is the creation of 2 peaks: the left one very thin, tall and pronounced, and the right one very wide, small and soften.
-When the $log{nH}$ is increased, the left peak starts to decrease while mixing with the right one, decreasing their height ratio until the left peak completely disappears.
+When the \lognh is increased, the left peak starts to decrease while mixing with the right one, decreasing their height ratio until the left peak completely disappears.
 The resulting spectrum, with high column density, is a wide single mountain with intensity significantly less than at the beginning.
@@
 \begin{center}
-  \includegraphics[width=0.5\textwidth]{./figures/influence_lognH.png}
+  \includegraphics[width=0.5\textwidth]{./figures/inf_lognh_soft.png}
 \end{center}
-\caption{\textbf{Influence of Outflow Hydrogen Column Density:} The values of the fixed parameters are \vel = 100 \kms and \ang = 90$^\circ$.
+\caption{\textbf{Influence of Outflow Hydrogen Column Density:} The values of the fixed parameters are \vout = $100$ \kms and \vgal = $100$ \kms.
 There are three stages of the \lognh value shown: initial, intermediate and final, with the values shown on the plot.\\
@@
 
-\subsubsection{Influence of the Outflow Expanding Velocity: \vel }
+\subsection{Influence of the Outflow Expanding Velocity: \vout }
 
 The effect of this parameter consists in a shift of the initial spectrum in the column density.
-The more \vel the outflow has, the more the spectrum simulates the previous velocity but with a greater \lognh.
+The more \vout the outflow has, the more the spectrum simulates the previous velocity but with a greater \lognh.
 If one compares with Fig.
@@
 \begin{center}
-  \includegraphics[width=0.5\textwidth]{./figures/influence_vel.png}
+  \includegraphics[width=0.5\textwidth]{./figures/inf_vout1_soft.png}
 \end{center}
-\caption{\textbf{Influence of Outflow Expanding Velocity:} The values of the fixed parameters are \lognh = 20.0625 and \ang = 90$^\circ$.
-If one increases \lognh for an outflow with \vel = 100 \kms it will create similar spectra to these in certain points.\\
-\label{fig:influence_vel}}
+\caption{\textbf{Influence of Outflow Expanding Velocity:} The values of the fixed parameters are \lognh = 20.125 and \vgal = $100$ \kms.\\
+\label{fig:influence_vout1}}
 \end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+  \includegraphics[width=0.5\textwidth]{./figures/inf_vout2_soft.png}
+\end{center}
+\caption{\textbf{Influence of Outflow Expanding Velocity:} The values of the fixed parameters are \lognh = 21.25 and \vgal = $100$ \kms.\\
+\label{fig:influence_vout2}}
+\end{figure}
+
+\subsection{Number of Peaks and Peaks Assymetry}
+
+---------------------------------------------------------------------\\
+MISSING: \\
+- Should I put this in results?
+-----------------------------------------------------------------------\\
 

### 2015-03-24 Simulation/SpectraVisualization.Rmd
change parameters values

@@
 ```{r, echo=FALSE}
+library(shiny)
 
 inputPanel(
-  sliderInput("v_galaxy", label = "Galaxy Velocity:",
-              min = 1, max = 4, value = 1, step = 1),
+  selectInput("v_galaxy", label = "Galaxy Velocity:", 
+              choices = c("60 km/s" = 60, "125 km/s" = 125), ),
 
-  sliderInput("v_outflow", label = "Outflow Velocity:",
-              min = 100, max = 500, value = 100, step = 100),
+  selectInput("v_outflow", label = "Outflow Velocity:", 
+              choices = c("100 km/s" = 100, "200 km/s" = 200), ),
 
@@
 
-  v_galaxy_options <- c(0, 20, 100, 200)
-
   lognh_options <- c(20.0, 20.0625, 20.125, 20.1875, 20.25, 20.3125, 20.375, 20.4375, 20.5, 20.5625, 20.625, 20.6875, 20.75, 20.8125, 20.875, 20.9375, 21.0, 21.0625, 21.125, 21.1875, 21.25, 21.3125, 21.375, 21.4375, 21.5, 21.5625, 21.625, 21.6875, 21.75, 21.8125, 21.875, 21.9375, 22.0, 22.0625, 22.125, 22.1875, 22.25, 22.3125, 22.375, 22.4375, 22.5)
@@
 
-  vg <- v_galaxy_options[input$v_galaxy]
+  vg <- input$v_galaxy
   vo <- input$v_outflow
@@
 
-  ggplot(spectrum_sub, aes(x=x,y=y)) + geom_line(col = 30, lw = 2) + labs(title=text, x="Lambda (A)", y="Intensity (Arbitrary Units)") + xlim(1210, 1232) + ylim(0, 7100) + theme(plot.title = element_text(hjust = 1, vjust = 1))
+  ggplot(spectrum_sub, aes(x=x,y=y)) + geom_line(col = 30, lw = 2) + labs(title=text, x="Velocity (km/s)", y="Intensity (Arbitrary Units)") + xlim(-1000, 4010) + ylim(0, 6500) + theme(plot.title = element_text(hjust = 1, vjust = 1))
 

### 2015-03-24 Simulation/SpecialPlots.R
Delete SpecialPlots.R

@@ -1,88 +1,0 @@
-library(ggplot2)
-
-spectrum <- read.csv("./data/galaxyoutflow.csv")
-
-#Variando log(nH)
-
-vg <- 100
-vo <- 100
-lnh <- c(20.125,20.5625,21.25,22.25)
-
-spectrum_sub <- spectrum[spectrum$v_gal==vg,]
-spectrum_sub <- spectrum_sub[spectrum_sub$v_out==vo,]
-#spectrum_sub <- spectrum_sub[spectrum_sub$lognh==lnh,]
-
-text = paste(c("v_out =", vo, "km/s \n", "v_gal =", vg, "km/s"), collapse=" ")
-
-df1 <- spectrum_sub[spectrum_sub$lognh==lnh[1],]
-df2 <- spectrum_sub[spectrum_sub$lognh==lnh[2],]
-df3 <- spectrum_sub[spectrum_sub$lognh==lnh[3],]
-df4 <- spectrum_sub[spectrum_sub$lognh==lnh[4],]
-
-ggplot(df1,aes(x,y)) + geom_line(aes(color="log(nH) = 20.125"), size=1.3)+
-  geom_line(data=df2,aes(color="log(nH) = 20.5625"), size=1.3)+
-  geom_line(data=df3,aes(color="log(nH) = 21.25"), size=1.3)+
-  geom_line(data=df4,aes(color="log(nH) = 22.25"), size=1.3)+
-  labs(x="Lambda (A)", y="Intensity (Arbitrary Units)", color=text, size = 40) + 
-  xlim(1210, 1227) + ylim(0, 7000) 
-
-#Variando v_out
-
-vg <- 100
-vo <- c(100,200,300)
-lnh <- c(20.125, 21.25)
-
-spectrum_sub_i <- spectrum[spectrum$v_gal==vg,]
-#spectrum_sub <- spectrum_sub[spectrum_sub$v_out==vo,]
-#spectrum_sub <- spectrum_sub[spectrum_sub$lognh==lnh,]
-
-spectrum_sub <- spectrum_sub_i[spectrum_sub_i$lognh==lnh[1],]
-text = paste(c("log(nH) =", lnh[1], "\n v_gal =", vg, "km/s"), collapse=" ")
-
-df1 <- spectrum_sub[spectrum_sub$v_out==vo[1],]
-df2 <- spectrum_sub[spectrum_sub$v_out==vo[2],]
[…]

### 2015-03-24 Simulation/WideRange/SpecialPlotsWideRange.R
simulation with a range much wider

@@ -1,0 +1,88 @@
+library(ggplot2)
+
+spectrum <- read.csv("./data/galaxyoutflow.csv")
+
+#Variando log(nH)
+
+vg <- 100
+vo <- 100
+lnh <- c(20.125,20.5625,21.25,22.25)
+
+spectrum_sub <- spectrum[spectrum$v_gal==vg,]
+spectrum_sub <- spectrum_sub[spectrum_sub$v_out==vo,]
+#spectrum_sub <- spectrum_sub[spectrum_sub$lognh==lnh,]
+
+text = paste(c("v_out =", vo, "km/s \n", "v_gal =", vg, "km/s"), collapse=" ")
+
+df1 <- spectrum_sub[spectrum_sub$lognh==lnh[1],]
+df2 <- spectrum_sub[spectrum_sub$lognh==lnh[2],]
+df3 <- spectrum_sub[spectrum_sub$lognh==lnh[3],]
+df4 <- spectrum_sub[spectrum_sub$lognh==lnh[4],]
+
+ggplot(df1,aes(x,y)) + geom_line(aes(color="log(nH) = 20.125"), size=1.3)+
+  geom_line(data=df2,aes(color="log(nH) = 20.5625"), size=1.3)+
+  geom_line(data=df3,aes(color="log(nH) = 21.25"), size=1.3)+
+  geom_line(data=df4,aes(color="log(nH) = 22.25"), size=1.3)+
+  labs(x="Lambda (A)", y="Intensity (Arbitrary Units)", color=text, size = 40) + 
+  xlim(1210, 1227) + ylim(0, 7000) 
+
+#Variando v_out
+
+vg <- 100
+vo <- c(100,200,300)
+lnh <- c(20.125, 21.25)
+
+spectrum_sub_i <- spectrum[spectrum$v_gal==vg,]
+#spectrum_sub <- spectrum_sub[spectrum_sub$v_out==vo,]
+#spectrum_sub <- spectrum_sub[spectrum_sub$lognh==lnh,]
+
+spectrum_sub <- spectrum_sub_i[spectrum_sub_i$lognh==lnh[1],]
+text = paste(c("log(nH) =", lnh[1], "\n v_gal =", vg, "km/s"), collapse=" ")
+
+df1 <- spectrum_sub[spectrum_sub$v_out==vo[1],]
+df2 <- spectrum_sub[spectrum_sub$v_out==vo[2],]
[…]

### 2015-09-17 Paper/ms.tex
updates, not complete

@@
 
-\cite{PartridgePeebles} predicted a population of galaxies with a strong Lyman Alpha (\lya) emission,  nowadays galaxies selected using the \lya line are known as Lyman Alpha Emitters (LAEs).
-Since the first observed LAE by \cite{DjorgovskiThompson} different teams have observed several LAEs \cite{Rhoads00,Gawiser2007,Koehler2007,Ouchi08,Yamada2012,Schenker2012,Kulas12, Yamada2012, Chonis2013,Finkelstein2013,Ostlin14} with the aim of exploring the extragalactic Universe.
-Specially at $z>=2$ since it is when the  line is redshifted into the optical regime.
-With the outcoming of new and powerful telescopes such as the James Webb Space Telescope new LAEs are going to be discovered with a better resolution and at
-higher redshifts.
+\cite{PartridgePeebles} predicted that young galaxies would have a strong Lyman Alpha (\lya) emission.
+Nowadays galaxies selected using the \lya line are known as Lyman Alpha Emitters (LAEs).
+Since the first observed LAE by \cite{DjorgovskiThompson} different teams have observed several LAEs \cite{Rhoads00,Gawiser2007,Koehler2007,Ouchi08,Yamada2012,Schenker2012,Kulas12, Yamada2012, Chonis2013,Finkelstein2013,Ostlin14} specially at $z\geq2$ since it is when the  line is redshifted into the optical regime.
+LAEs became then a tool to explore the extragalactic Universe and with upcoming telescopes such as the James Webb Space Telescope, new ones are going to be discovered with a better resolution and at higher redshifts.
+This creates then, a clear motivation to model and observe them.
+\\
 
-This observations have a direct impact in studying the reionization epoch see \cite{review} fore more details and references in within, properties of the interstellar medium (ISM) and the intergalactic medium (IGM) \citep{Behrens13} \citep{DijkstraKramer}, constraining star formation rates of high redshift galaxies, understanding galaxy luminosity functions \cite{Max} and studying the large scale structure of the Universe.
-In all of this
-studies is required an understanding of the processes that model the morphology and the radiate transfer process 
-behind  of the \lya line.
+These observations have a direct impact in studying the reionization epoch \cite{review}, properties of the interstellar medium (ISM) and the intergalactic medium (IGM) \citep{Behrens13} \citep{DijkstraKramer}, constraining star formation rates of high redshift galaxies, understanding galaxy luminosity functions \cite{Max} and studying the large scale structure of the Universe.
+In all of these
+studies, an understanding of the processes that model the morphology and the radiate transfer process behind  of the \lya line, is required.
+To fully understand the observed spectra of the LAEs, these galaxies must be modeled.
+\\
 
-To fully understand the observed spectra of the LAEs this galaxies must be modeled.
 However the resonant nature of the line makes this a challenging task.
-Analytical solutions for the outcoming spectra in simple ISM static
-geometries have been derived \cite{Adams72, Harrington73, Neufeld90, Dijkstra06}.
-Radiative transfer codes \citep{DijkstraKramer, Laursen09, Verhamme06, CLARA} have been developed in order to understand the effect of the gas kinematics in the \lya line, special attention have been devoted to  the effects of clumpy media \citep{Hansen06} and expanding/contracting shell/spherical geometries started to be studied \citep{Ahn03,Verhamme06,Dijkstra06}.
-Recently \cite{Garavito14} have studied in detail the effect of rotation on the lyman alpha line.Hydrodynamic simulations have studied the outcomming spectra of LAEs in large scale simulations \cite{Forero12}.
-Recently Monte Carlo codes have been used in hydrodynamic simulations to study in detail individual galaxies \citep{Laursen09,Barnes11,Verhamme12,Yajima12}.
+Analytical solutions for the outcoming spectra in simple ISM static geometries have been derived \cite{Adams72, Harrington73, Neufeld90, Dijkstra06}.
+Radiative transfer codes \citep{DijkstraKramer, Laursen09, Verhamme06, CLARA} have been developed in order to understand the effect of the gas kinematics in the \lya line.
+Special attention have been devoted to  the effects of clumpy media \citep{Hansen06} and expanding/contracting shell/spherical geometries started to be studied \citep{Ahn03,Verhamme06,Dijkstra06}.
+Recently, a rotation model, created by Garavito et al.
+\cite{Garavito14} models
+a rotating spherical galaxy with homogeneous gas mixture and analyzes that impact in the \lya line.
+Hydrodynamic simulations have studied the outcomming spectra of LAEs in large scale simulations \cite{Forero12}.
+And Monte Carlo codes have been used in hydrodynamic simulations to study in detail individual galaxies \citep{Laursen09,Barnes11,Verhamme12,Yajima12}.\\
 
-Especial attention have been devoted to model the presence of outflows in the galaxy, motivates by previous observational studies*.
+Special attention have been devoted to model the presence of outflows in the galaxy, motivated by previous observational studies.
 Outflows are a consequence of the interstellar medium (ISM) being ejected from the galaxy due to supernova explosions.
@@
 \citep{Behrens2014}.
+Despite the fact that outflows have been broadly studied, rotation should also be present in this galaxies.
+The joint effect of the above properties should have a direct impact on the morphology of the \lya line.
+This is the subject of this work.
+\\
 
-Despite the fact that outflows have been broadly studied rotation should also be present in this galaxies. The joint 
-effect of the two above properties should have a direct effect on the morphology of the \lya line.
+CAMBIAR ESTOOOOO\\
 
-Study this effect is the main motivation of this paper in which we combine the effect of rotation followed by an outflow.
-We proposed a simplified model in which the galaxy is modeled as an sphere undergoing solid-body rotation, with an homogeneous mixture of dust and hydrogen at a constant temperature.
-
+We propose a simplified model in which the galaxy is modeled as an sphere undergoing solid-body rotation, with an homogeneous mixture of dust and hydrogen at a constant temperature.
 The solid-body rotation does not induce any spatial anisotropy in the integrated line flux, the escape fraction or in the average number of scatterings.
@@
 In this model the optical depth $\tau_{H}$, the  rotation velocity $V_{max}$ and the inclination angle $\theta$ are free parameters.
+\\
 
-The outcoming spectra of the rotating galaxy is then affected by a symmetric thin shell of expanding gas at a constant velocity following the model proposed by \cite{2014arXiv1404.2958V, Orsi12}.
+The outcoming spectra of the rotating galaxy is then affected by a symmetric thin shell of expanding gas at a constant velocity following the model proposed by \cite{2014arXiv1404.2958V, Orsi12}.   \\
 
@@
 In \S \ref{sec:results} we present the results of our model.
-In \S \ref{sec:discussion} we compare our results with recent observations of LAEs with special attention of
-those morphologies that present features of galaxy rotation and outflows. In the latest section we present our conclusions.
-
-%LAEs are young and far away galaxies with most of its matter composed
-%by Hydrogen atoms, being the rest heavier elements, like Iron,
-%produced by growing stars burning their material. Then, this spectral
-%line tells very important information about the galaxy, most of it
-%actually, which creates a motivation to find a way to model the \lya
-%line according to certain free parameters that vary from a galaxy to
-%another and that can be obtained from observations. \\
-
-%Our purpose in this paper is then to make a theoretical model, based
-%on radiative transfer simulations, that use MonteCarlo 
-%computational methods to emulate how the line profile is going to
-%come out of the galaxy if it is rotating and has a surrounding 
-%outflow, both of this phenomena characterized by key parameters that
-%are going to be described further on the paper. \\
-
-%As it has been described, the main purpose of this project is to mix
-%a rotating galaxy with an external outflow surrounding it and analyze
-%the resulting spectrum. The rotation model for the LAE consists on a
-%sphere with an homogeneous mixture of dust and hydrogen at a constant
-%temperature undergoing a solid-body rotation. The spectrum then
-%depends on the maximum velocity of the sphere, the neutral hydrogen
-%optical depths and the viewing angle. What happens is that photons
-%are emitted from a central distribution of gas and escape the sphere
-%after a radiative transfer process that ends at the border.\\
-
-%In this model, rotation does not induce any spatial anisotropy in the
-%integrated line flux, the escape fraction or the average 
-%number of scatterings, which led to the creation of an analytic
-%approximation for the galaxy spectrum. This mathematical expression 
-%helps to minimize the computational costs and lets try with several
-%parameters without spending great amounts of time running the
-%code. \\
-
-%After this photons escape the galaxy to empty space, they encounter a thin spherical shell of matter at a certain radius from the
-%center. That material is the outflow of the LAE, created mainly by
-%starbursts which composition is characterized with the parameters of
-%Hydrogen column density and metallicity. Besides its components, the
-%galactic outflow is also defined by an expanding constant velocity
-%that affects the redshift of the photons.\\
-
-%As there is a lot of empty space inside the shell, it acts as a
-%reflector of photons. This means, that when one wants to comes out it
-%is most likely to bounce inside the sphere several times before
-%finally escaping. However it is not likely that the photon comes back
-%again inside the galaxy, which helps that the first process does not
-%have to be repeated, and both stages can be treated as consecutive,
-%not simultaneous. \\
+In \S \ref{sec:discussion} we compare our results with recent observations of LAEs with special attention of those morphologies that present features of galaxy rotation and outflows.
+In the latest section we present our conclusions.
+\\
 
@@
 We use the simplified rotation model developed by \citep{Garavito14} in which a rotating galaxy is modeled as a solid rotating sphere, with a homogeneous mixture of hydrogen and dust.
-Photons can be initially at the center or can be homogeneously distributed inside the sphere.
-The equations governing this solid-body rotation sphere in
-which the axis of rotation is defined to be align with the $z$-axis are:
+Photons are initially at the center of the sphere.
+The equations governing this solid-body rotation sphere in which the axis of rotation is defined to be align with the $z$-axis are: \\
+
+CAMBIAR ESTOOOOO
 
@@
 In this case we take the angular velocity in the same direction as the $\hat{k}$ unit vector.
+\\
+
+(...) At the end only a fraction of those manage to get out of the outflow and their wavelengths are measured to find the
+final spectrum.
+In order to simulate all the possible cases we set some key parameters for the program to vary, and some others fixed which are defined by the characteristics of LAEs.
+This are chosen as follows.\\
+
+\subsubsection{Galaxy Parameters}
+
+Our aim is to provide a realistic baseline to compare against observations of LAES at $z\sim 3$.
+It has been found by analysis of the abundance and angular correlation function that LAES reside in DM halos of masses in the range $10^{10}-10^{11}$\Msun \cite{WalkerSoler2012}.
+This mass range corresponds to maximum circular velocities in the range $60-125$\kms and a median halo scale radius of $15$kpc.
+\footnote{These results were found using the  N-body data available in \url{www.cosmosim.org}}.
+\\
+
+These galaxies have gas fractions close to $20\%$ \citep{Narayanan2012}. We approximate that the hydrogen content is
+$20\%$ the total baryonic content from the cosmological baryon to dark matter  abundances $\Omega_b/\Omega_{dm}=0.1825$ \citep{Planck2015}, multiplied by a primordial Hydrogen fraction of $0.75$.
+All these considerations gives us hydrogen masses in the range $2.7\times 10^{8}-2.7\times 10^{9}$\Msun.\\
+
+CAMBIAR ESTOOOOO\\
+
+These choices give us a range for the number density of Hydrogen atoms of $4\times10^{-4}-4\times 10^{-3}$ atoms cm$^{-3}$.
+With a Lyman-$\alpha$ cross section at the line center of $\sigma_{H}=1.0\times 10^{-14}$ cm$^{2}$ we finally obtain that the optical depth from the cloud's center  should be in the range $\tau=2 \times 10^{5} - 2 \times 10^{6}$.
+\\
+
+From these constraints we chose to model two kinds of central galaxies in the extremes of these distributions.
+The first has $\tau =2\times 10^5$ and a rotational velocity of $60$\kms.
+The second has $\tau=2\times 10^6$ and a rotational velocity of $125$\kms.\\
+
+For the first stage there are two fixed parameters: the optical depth $\tau = 10^8$ and the galaxy viewing angle \ang = $90^\circ$.
+For the second stage there is one fixed parameter: the metallicity of the outflow $Z=-4.0$.
+This 3 fixed values are selected because the characteristics of observed LAEs, especially their low mass and their
+highest star formation rate of all. \\
+
+We have then 3 parameters left that are going to vary along a wide range.
+These are: the galaxy rotation velocity \vgal, the outflow hydrogen column density \nh and the outflow expanding velocity \vout.\\
+
+\vgal covers 3 different angles: $20$ \kms, $100$ \kms and $200$ \kms.
+\lognh takes 41 different values from $20.0$ to $22.5$.
+And \vout covers 5 equidistant velocities from $100$ \kms to $500$ \kms.
+The permutations of these three are analyzed in section \ref{sec:results}.
+\\
+
+The results of this project consist of emulating a LAE spectrum basing on its physical characteristics defined by the 3 free parameters we stated before.
+When defined the combination of those three.
+\\
+
+In the following subsection each free parameter is explained deeper. \\
+
+In order to study the influence of each of the three free parameters, we fix two of them and see how the final spectrum varies along the other one left. In each case we will state these changes. \\
+
+\subsection{Influence of the Galaxy Rotation Velocity: \vgal}
+
+\subsection{Influence of the Galaxy Outflow Velocity: \vout }
+
+\subsection{Influence of the Galaxy Optical Depth: $\tau$ }
+
+\subsection{Number of Peaks and Peaks Assymetry}
+
+\section{Discussion}
+\label{sec:discussion}
+
+---------------------------------------------------------------------\\
+MISSING: \\
+- Comparison with some other result (probably observations).\\
+- Why is this result useful? \\
+- What possible implications can this model have?\\
+-----------------------------------------------------------------------\\
+
+\section{Conclusions}
+\label{sec:conclusions}
+Here goes the conclusions....
+
+\section*{Acknowledgments}
+
+We acknowledge Alvaro Orsi and Julian Mejia for collaborating with us offering their time, advice and especially data. We used their outflow simulations in order to get our results.\\
+
+The data, source code and instructions to replicate the results of this paper can be found here {\texttt{https://github.com/mariacamilaremolinagutierrez/ LymanAlpha/}}.
+Most of our code benefits from the work of the IPython and Matplotlib communities \citep{IPython,matplotlib}.\\
+
+---------------------------------------------------------------------\\
+MISSING: \\
+- More acknowledgments.\\
+-----------------------------------------------------------------------\\
+
+%------------------------REFERENCES----------------------------
+
+\bibliographystyle{latex/apj}
+\bibliography{references}
+
+\newpage
+
+%------------------------APPENDIX----------------------------
+
+\appendix
+\section{Thin Shell Outflow}
+
+In this section we describe the two different models that together are used to reproduce a real and consistent \lya profile.
+The first one is a rotation model for the galaxy and the second is a thin shell model for the outflow.
+\\
+
+\subsection{Rotation Model}
+
+We use the simplified rotation model developed by \citep{Garavito14} in which a rotating galaxy is modeled as a solid rotating sphere, with a homogeneous mixture of hydrogen and dust.
+Photons can be initially at the center or can be homogeneously distributed inside the sphere.
+The equations governing this solid-body rotation sphere in
+which the axis of rotation is defined to be align with the $z$-axis are: \\
+
+\begin{equation}
+v_{x}=-\frac{y}{R}V_{\rm max}, \label{subeq1}
+\end{equation}
+
+\begin{equation}
+v_{y}=\frac{x}{R}V_{\rm max}, \label{subeq2}
+\end{equation}
+
+\begin{equation}
+v_{z}=0, \label{subeq3}
+\end{equation}
+
+Where $R$ is the radius of the sphere and $V_{\rm max}$ is the linear velocity at the sphere's surface.
+The minus/plus sign in the $x$/$y$-component of the velocity indicates the direction of rotation.
+In this case we take the angular velocity in the same direction as the $\hat{k}$ unit vector.\\
 
 In this work we use the analytical expression for rotation derived in \citep{Garavito14} where a rotating sphere can be seen as a static sphere in the laboratory frame with a bulk velocity difference in each surface element with respect to a distant observer.
-With the previous analysis the outcoming spectra can be expressed as:
+With the previous analysis the outcoming spectra can be expressed as:\\
 
@@
 The outflow consists of an isothermal, spherical flow expanding at
-constant velocity \vel.  The outflow is empty inside the shell's inner radius $R_{in}$ and
-reaches out to an external radius $R_{out}$. The relationship between these two radii is parameterized by $R_{in} =
+constant velocity \vel.
+The outflow is empty inside the shell's inner radius $R_{in}$ and reaches out to an external radius $R_{out}$.
+The relationship between these two radii is parameterized by $R_{in} =
 f_{th}R_{out}$, with $f_{th}=0.9$ as the fiducial value.
 The temperature of the medium is assumed constant and equal to $T=10^4 K$ which sets the velocity dispersion of Maxwell-Boltzmann distributions to $v_{\rm th}=12.84$\kms.
+\\
 
-The gas has an homogeneous Hydrogen number density inside the flow. The total mass inside the shell is parameterized by its column density
+The gas has an homogeneous Hydrogen number density inside the flow. The total mass inside the shell is parameterized by its column density\\
 
@@
 %
-where $M_{shell}$ is the outflow mass, $m_H$ is the mass of the hydrogen atom and $X_H=0.74$ is the fraction of hydrogen in the cold gas.
+where $M_{shell}$ is the outflow mass, $m_H$ is the mass of the hydrogen atom and $X_H=0.74$ is the fraction of hydrogen in the cold gas.\\
 
 The outflow also includes dust homogeneously mixed with the gas. The dust optical depth $\tau_d$ is parameterized by the metallicity of the cold gas $\langle Z_{cold} \rangle$:
+
 \begin{equation}
@@
 \end{equation}
-
-%We choose this model because it h
-%for two main reasons. First, when we
-%analyze observed spectra we can se that the line is spread around the
-%place where line should be when already taking into account the
-%redshift due to the distance to the LAE. This implies that the photons
-%before escaping the composed system suffer a change in frequency
-%themselves, which we explain by making them rebound over the inner
-%surface of the shell such as some of them suffer blueshift and other
-%redshift, that even small, is significant and observed.
-
-%The second reason is because as the space between the shell and the
-%galaxy is said to be void, the photons that escape from it suffer the
-%scattering process at a far distance from the center, in a way such as
-%if they rebound the chances that it happens in the normal direction to
-%the surface are lower than in any other model. This implies that the
-%photons are less likely to re-enter the galaxy so there is no need to
-%start the diffusion inside again, allowing us to divide the spectrum
-%creation process into 2 independent events, saving computational time
-%and simplifying the model to its best.
 
@@
 What happens is that the photons that escaped the galaxy enter now into the outflow with the same radial direction that they came out with.
-At the end only a fraction of those manage to get out of the outflow and their wavelengths are measured to find the
-final spectrum.
+At the end only a fraction of those manage to get out of the outflow and their wavelengths are measured to find the final spectrum.
+\\
 
@@
 
-In order to simulate all the possible cases we set some key parameters for the program to vary, and some others fixed which are defined by the characteristics of LAEs. This are chosen as follows.
+In order to simulate all the possible cases we set some key parameters for the program to vary, and some others fixed which are defined by the characteristics of LAEs. This are chosen as follows.\\
 
@@
 Our aim is to provide a realistic baseline to compare against observations of LAES at $z\sim 3$.
-It has been found by analysis of the abundance and angular correlation function that LAES reside in DM halos of masses in the range
-$10^{10}-10^{11}$\Msun \cite{WalkerSoler2012}. This mass range corresponds to maximum circular velocities in the
-range $60-125$\kms and a median halo scale radius of $15$kpc.  \footnote{These results were found using the  N-body data available in \url{www.cosmosim.org}}.
+It has been found by analysis of the abundance and angular correlation function that LAES reside in DM halos of masses in the range $10^{10}-10^{11}$\Msun \cite{WalkerSoler2012}.
+This mass range corresponds to maximum circular velocities in the range $60-125$\kms and a median halo scale radius of $15$kpc.
+\footnote{These results were found using the  N-body data available in \url{www.cosmosim.org}}.
+\\
 
@@
 $20\%$ the total baryonic content from the cosmological baryon to dark matter  abundances $\Omega_b/\Omega_{dm}=0.1825$ \citep{Planck2015}, multiplied by a primordial Hydrogen fraction of $0.75$.
-All these considerations gives us hydrogen masses in the range $2.7\times 10^{8}-2.7\times 10^{9}$\Msun.
+All these considerations gives us hydrogen masses in the range $2.7\times 10^{8}-2.7\times 10^{9}$\Msun. \\
 
@@
 With a Lyman-$\alpha$ cross section at the line center of $\sigma_{H}=1.0\times 10^{-14}$ cm$^{2}$ we finally obtain that the optical depth from the cloud's center  should be in the range $\tau=2 \times 10^{5} - 2 \times 10^{6}$.
+\\
 
@@
 The first has $\tau =2\times 10^5$ and a raotational velocity of $60$\kms.
-The second has $\tau=2\times 10^6$ and a rotational velocity of $125$\kms.
+The second has $\tau=2\times 10^6$ and a rotational velocity of $125$\kms.\\
 
@@
 This 3 fixed values are selected because the characteristics of observed LAEs, especially their low mass and their
-highest star formation rate of all.
+highest star formation rate of all. \\
 
@@
 These are: the galaxy rotation velocity \vgal, the outflow hydrogen column density \nh and the outflow expanding velocity \vout.
+\\
 
@@
 The permutations of these three are analyzed in section \ref{sec:results}.
+\\
 
@@
 
----------------------------------------------------------------------\\
-MISSING: \\
-- What are the compact results.\\
-- Not a physical analysis yet. \\
-- Write better (prettier)\\
------------------------------------------------------------------------\\
-
 In the following subsection each free parameter is explained deeper. \\
 
-In order to study the influence of each of the three free parameters, we fix two of them and see how the final spectrum varies along the other one left. In each case we will state these changes.
+In order to study the influence of each of the three free parameters, we fix two of them and see how the final spectrum varies along the other one left. In each case we will state these changes.\\
 
@@
 Fig.
-\ref{fig:influence_vgal} helps visualize this effect in a better way.
+\ref{fig:influence_vgal} helps visualize this effect in a better way.\\
 
@@
 Fig.
-\ref{fig:influence_lognH} helps visualize this effect in a better way.
+\ref{fig:influence_lognH} helps visualize this effect in a better way.\\
 
@@
 \ref{fig:influence_lognH} the similarities are really clear.
+\\
 
@@
 \end{figure}
-
-\subsection{Number of Peaks and Peaks Assymetry}
-
----------------------------------------------------------------------\\
-MISSING: \\
-- Should I put this in results?
------------------------------------------------------------------------\\
-
-\section{Discussion}
-\label{sec:discussion}
-
----------------------------------------------------------------------\\
-MISSING: \\
-- Comparison with some other result (probably observations).\\
-- Why is this result useful? \\
-- What possible implications can this model have?\\
------------------------------------------------------------------------\\
-
-Ideas: \\
-
-The decrease of the intensity while increasing the column density is caused because the second is proportional to the absorption of light in the gas.
-The more \lognh, the less photons get out of the outflow.
-
-\section{Conclusions}
-\label{sec:conclusions}
-Here goes the conclusions....
-
-\section*{Acknowledgments}
-
-We acknowledge Alvaro Orsi and Julian Mejia for collaborating with us offering their time, advice and especially data. We used their outflow simulations in order to get our results.\\
-
-The data, source code and instructions to replicate the results of this paper can be found here {\texttt{https://github.com/mariacamilaremolinagutierrez/ LymanAlpha/}}.
-Most of our code benefits from the work of the IPython and Matplotlib communities \citep{IPython,matplotlib}.\\
-
----------------------------------------------------------------------\\
-MISSING: \\
-- More acknowledgments.\\
------------------------------------------------------------------------\\
-
-\bibliographystyle{latex/apj}
-\bibliography{references}
-
-\newpage
 

### 2015-09-18 Paper/ms.tex
updates

@@
 
-CAMBIAR ESTOOOOO\\
-
-We propose a simplified model in which the galaxy is modeled as an sphere undergoing solid-body rotation, with an homogeneous mixture of dust and hydrogen at a constant temperature.
-The solid-body rotation does not induce any spatial anisotropy in the integrated line flux, the escape fraction or in the average number of scatterings.
-This symmetry allows to the creation of an analytic approximation for the galaxy spectrum  proposed, see \cite{Garavito14} for details.
-In this model the optical depth $\tau_{H}$, the  rotation velocity $V_{max}$ and the inclination angle $\theta$ are free parameters.
+We propose a simplified model in which the galaxy is modeled as an sphere undergoing solid-body rotation, with an homogeneous mixture of dust and hydrogen at a constant temperature, that is also expanding in the radial direction due to outflows.
+In this model the optical depth \tauh, the  rotation velocity \vrot and the outflow velocity \vout are free parameters.
 \\
 
-The outcoming spectra of the rotating galaxy is then affected by a symmetric thin shell of expanding gas at a constant velocity following the model proposed by \cite{2014arXiv1404.2958V, Orsi12}.   \\
+CAMBIAR ESTOOOOO\\
 
@@
 \label{sec:theo}
-In this section we describe the two different models that together are used to reproduce a real and consistent \lya profile.
-The first one is a rotation model for the galaxy and the second is a thin shell model for the outflow.
-\\
+In this section we describe the proposed model used to reproduce a real and consistent \lya profile. \\
 
-\subsection{Rotation Model}
+\subsection{Model}
 
 We use the simplified rotation model developed by \citep{Garavito14} in which a rotating galaxy is modeled as a solid rotating sphere, with a homogeneous mixture of hydrogen and dust.
+There is also the radial expanding velocity.
 Photons are initially at the center of the sphere.
-The equations governing this solid-body rotation sphere in which the axis of rotation is defined to be align with the $z$-axis are: \\
-
-CAMBIAR ESTOOOOO
+These two velocities are added by components as follows.
+The equations governing this movement in which the axis of rotation is defined to be align with the $z$-axis are: \\
 
 \begin{equation}
-v_{x}=-\frac{y}{R}V_{\rm max}, \label{subeq1}
+v_{x}=\frac{x}{R}v_{\rm out}-\frac{y}{R}v_{\rm rot}, \label{subeq1}
 \end{equation}
@@
 \begin{equation}
-v_{y}=\frac{x}{R}V_{\rm max}, \label{subeq2}
+v_{y}=\frac{y}{R}v_{\rm out}+\frac{x}{R}v_{\rm rot}, \label{subeq2}
 \end{equation}
@@
 \begin{equation}
-v_{z}=0, \label{subeq3}
+v_{z}=\frac{z}{R}v_{\rm out}, \label{subeq3}
 \end{equation}
 
-Where $R$ is the radius of the sphere and $V_{\rm max}$ is the linear velocity at the sphere's surface.
-The minus/plus sign in the $x$/$y$-component of the velocity indicates the direction of rotation.
+Where $R$ is the radius of the sphere.
+The minus/plus sign in the $x$/$y$-component of the rotation velocity part indicates the direction of rotation.
 In this case we take the angular velocity in the same direction as the $\hat{k}$ unit vector.
@@
 
-(...) At the end only a fraction of those manage to get out of the outflow and their wavelengths are measured to find the
-final spectrum.
+CAMBIAR ESTOOOOO\\
+
+(...) At the end only a fraction of those manage to get out of the outflow and their wavelengths are measured to find the final spectrum.
 In order to simulate all the possible cases we set some key parameters for the program to vary, and some others fixed which are defined by the characteristics of LAEs.
@@
 
-\subsubsection{Galaxy Parameters}
+\subsection{Galaxy Parameters}
 
-Our aim is to provide a realistic baseline to compare against observations of LAES at $z\sim 3$.
-It has been found by analysis of the abundance and angular correlation function that LAES reside in DM halos of masses in the range $10^{10}-10^{11}$\Msun \cite{WalkerSoler2012}.
+Our aim is to provide a realistic baseline to compare against observations of LAEs at $z\sim 3$.
+It has been found by analysis of the abundance and angular correlation function that LAEs reside in DM halos of masses in the range $10^{10}-10^{11}$\Msun \cite{WalkerSoler2012}.
 This mass range corresponds to maximum circular velocities in the range $60-125$\kms and a median halo scale radius of $15$kpc.
@@
 
-These galaxies have gas fractions close to $20\%$ \citep{Narayanan2012}. We approximate that the hydrogen content is
-$20\%$ the total baryonic content from the cosmological baryon to dark matter  abundances $\Omega_b/\Omega_{dm}=0.1825$ \citep{Planck2015}, multiplied by a primordial Hydrogen fraction of $0.75$.
-All these considerations gives us hydrogen masses in the range $2.7\times 10^{8}-2.7\times 10^{9}$\Msun.\\
+CAMBIAR ESTOOOOO (cambie 10E9 por 10E10)\\
 
-CAMBIAR ESTOOOOO\\
+These galaxies have gas fractions close to $20\%$ \citep{Narayanan2012}.
+We approximate that the hydrogen content is $20\%$ the total baryonic content from the cosmological baryon to dark matter  abundances $\Omega_b/\Omega_{dm}=0.1825$ \citep{Planck2015}, multiplied by a primordial Hydrogen fraction of $0.75$.
+All these considerations gives us hydrogen masses in the range $2.7\times 10^{8}-2.7\times 10^{10}$\Msun.\\
 
 These choices give us a range for the number density of Hydrogen atoms of $4\times10^{-4}-4\times 10^{-3}$ atoms cm$^{-3}$.
-With a Lyman-$\alpha$ cross section at the line center of $\sigma_{H}=1.0\times 10^{-14}$ cm$^{2}$ we finally obtain that the optical depth from the cloud's center  should be in the range $\tau=2 \times 10^{5} - 2 \times 10^{6}$.
+With a Lyman-$\alpha$ cross section at the line center of $\sigma_{H}=1.0\times 10^{-14}$ cm$^{2}$ we finally obtain that the optical depth from the cloud's center  should be in the range $\tau_{\rm H}=2 \times 10^{5} - 2 \times 10^{7}$.
 \\
 
-From these constraints we chose to model two kinds of central galaxies in the extremes of these distributions.
+In order to be able to tell the influence of the rotation and outflow velocities in the \lya line morphology, a mapping of them is made without concerning of their physical meaning at first.
+The following ranges are selected for these parameters: \vrot in $0,100,200,300$ \kms and \vout in $100,200,300$ \kms.\\
+
+%From these constraints we chose to model two kinds of central galaxies in the extremes of these distributions.
 The first has $\tau =2\times 10^5$ and a rotational velocity of $60$\kms.
@@
 
-For the first stage there are two fixed parameters: the optical depth $\tau = 10^8$ and the galaxy viewing angle \ang = $90^\circ$.
+%For the first stage there are two fixed parameters: the optical depth $\tau = 10^8$ and the galaxy viewing angle \ang = $90^\circ$.
 For the second stage there is one fixed parameter: the metallicity of the outflow $Z=-4.0$.
-This 3 fixed values are selected because the characteristics of observed LAEs, especially their low mass and their
-highest star formation rate of all. \\
+This 3 fixed values are selected because the characteristics of observed LAEs, especially their low mass and their highest star formation rate of all.
+\\
 
-We have then 3 parameters left that are going to vary along a wide range.
-These are: the galaxy rotation velocity \vgal, the outflow hydrogen column density \nh and the outflow expanding velocity \vout.\\
+%We have then 3 parameters left that are going to vary along a wide range.
+These are: the galaxy rotation velocity \vrot, the outflow hydrogen column density \nh and the outflow expanding velocity \vout.\\
 
-\vgal covers 3 different angles: $20$ \kms, $100$ \kms and $200$ \kms.
+%\vrot covers 3 different angles: $20$ \kms, $100$ \kms and $200$ \kms.
 \lognh takes 41 different values from $20.0$ to $22.5$.
@@
 
-The results of this project consist of emulating a LAE spectrum basing on its physical characteristics defined by the 3 free parameters we stated before.
+%The results of this project consist of emulating a LAE spectrum basing on its physical characteristics defined by the 3 free parameters we stated before.
 When defined the combination of those three.
@@
 
-In the following subsection each free parameter is explained deeper. \\
+%In the following subsection each free parameter is explained deeper. \\
 
-In order to study the influence of each of the three free parameters, we fix two of them and see how the final spectrum varies along the other one left. In each case we will state these changes. \\
+%In order to study the influence of each of the three free parameters, we fix two of them and see how the final spectrum varies along the other one left. In each case we will state these changes. \\
 
-\subsection{Influence of the Galaxy Rotation Velocity: \vgal}
+\section{Results}
 
-\subsection{Influence of the Galaxy Outflow Velocity: \vout }
+\begin{figure}[h!]
+\begin{center}
+  \includegraphics[width=0.5\textwidth]{./figures/tau10E5.png}
+\end{center}
+\caption{\textbf{\lya profile for \tauh$=10^5$:} With \vrot ranging $0,100,200,300$ \kms and \vout ranging $100,200,300$ \kms.
+\label{fig:tau10E5}}
+\end{figure}
 
-\subsection{Influence of the Galaxy Optical Depth: $\tau$ }
+\begin{figure}[h!]
+\begin{center}
+  \includegraphics[width=0.5\textwidth]{./figures/tau10E6.png}
+\end{center}
+\caption{\textbf{\lya profile for \tauh$=10^6$:} With \vrot ranging $0,100,200,300$ \kms and \vout ranging $100,200,300$ \kms.
+\label{fig:tau10E6}}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+  \includegraphics[width=0.5\textwidth]{./figures/tau10E7.png}
+\end{center}
+\caption{\textbf{\lya profile for \tauh$=10^7$:} With \vrot ranging $0,100,200,300$ \kms and \vout ranging $100,200,300$ \kms.
+\label{fig:tau10E7}}
+\end{figure}
+
+\subsection{Influence of the Galaxy Rotation Velocity: \vrot}
+
+\subsection{Influence of the Galaxy Outflow Velocity: \vout}
+
+\subsection{Influence of the Galaxy Optical Depth: \tauh}
 
@@
 ---------------------------------------------------------------------\\
-MISSING: \\
+TO ADD: \\
 - Comparison with some other result (probably observations).\\
@@
 The outflow consists of an isothermal, spherical flow expanding at
-constant velocity \vel.
+constant velocity \vout.
 The outflow is empty inside the shell's inner radius $R_{in}$ and reaches out to an external radius $R_{out}$.
@@
 We have then 3 parameters left that are going to vary along a wide range.
-These are: the galaxy rotation velocity \vgal, the outflow hydrogen column density \nh and the outflow expanding velocity \vout.
+These are: the galaxy rotation velocity \vrot, the outflow hydrogen column density \nh and the outflow expanding velocity \vout.
 \\
 
-\vgal covers 3 different angles: $20$ \kms, $100$ \kms and $200$ \kms.
+\vrot covers 3 different angles: $20$ \kms, $100$ \kms and $200$ \kms.
 \lognh takes 41 different values from $20.0$ to $22.5$.
@@
 
-\subsection{Influence of the Galaxy Rotation Velocity: \vgal}
+\subsection{Influence of the Galaxy Rotation Velocity: \vrot}
 
@@
 Fig.
-\ref{fig:influence_vgal} helps visualize this effect in a better way.\\
+\ref{fig:influence_vrot} helps visualize this effect in a better way.\\
 
@@
 The increase is visible as well as its small enlargement factor.\\
-\label{fig:influence_vgal}}
+\label{fig:influence_vrot}}
 \end{figure}
@@
 \end{center}
-\caption{\textbf{Influence of Outflow Hydrogen Column Density:} The values of the fixed parameters are \vout = $100$ \kms and \vgal = $100$ \kms.
+\caption{\textbf{Influence of Outflow Hydrogen Column Density:} The values of the fixed parameters are \vout = $100$ \kms and \vrot = $100$ \kms.
 There are three stages of the \lognh value shown: initial, intermediate and final, with the values shown on the plot.\\
@@
 \end{center}
-\caption{\textbf{Influence of Outflow Expanding Velocity:} The values of the fixed parameters are \lognh = 20.125 and \vgal = $100$ \kms.\\
+\caption{\textbf{Influence of Outflow Expanding Velocity:} The values of the fixed parameters are \lognh = 20.125 and \vrot = $100$ \kms.\\
 \label{fig:influence_vout1}}
@@
 \end{center}
-\caption{\textbf{Influence of Outflow Expanding Velocity:} The values of the fixed parameters are \lognh = 21.25 and \vgal = $100$ \kms.\\
+\caption{\textbf{Influence of Outflow Expanding Velocity:} The values of the fixed parameters are \lognh = 21.25 and \vrot = $100$ \kms.\\
 \label{fig:influence_vout2}}

### 2015-11-04 Paper/ms.tex
introduction

@@
 
-\title{Titulo}
-\shorttitle{shorttitle}
+\title{Influence of galaxy rotation and outflows in the Lyman-$\alpha$ spectral line}
+\shorttitle{Influence of galaxy rotation and outflows in the Lyman-$\alpha$ spectral line}
 
@@
 
-\author{Maria Camila Remolina-Gutierrez, Jaime E. Forero-Romero \&
-  Juan N. Garavito-Camargo} 
-\affil{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
-No. 18A-10, Edificio Ip, Bogot\'a, Colombia}
-\author{Julian Mej\'ia}
-\affil{Chile}
-\author{Alvaro Orsi}
-\affil{Spain}
+\author{Maria Camila Remolina-Gutierrez, Jaime E. Forero-Romero \& Juan N. Garavito-Camargo} 
+\affil{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia}
 \email{mc.remolina197@uniandes.edu.co}
@@
 
-\keywords{Galaxies: high-redshift, Lyman Alpha Emission, Galaxy
-  Rotation, Galaxy Outflows ....MISSING....}
+\keywords{Galaxies: high-redshift, Lyman Alpha Emission, Galaxy Rotation, Galaxy Outflows, Radiative Transfer}
 
@@
 
-\cite{PartridgePeebles} predicted that young galaxies would have a strong Lyman Alpha (\lya) emission.
-Nowadays galaxies selected using the \lya line are known as Lyman Alpha Emitters (LAEs).
-Since the first observed LAE by \cite{DjorgovskiThompson} different teams have observed several LAEs \cite{Rhoads00,Gawiser2007,Koehler2007,Ouchi08,Yamada2012,Schenker2012,Kulas12, Yamada2012, Chonis2013,Finkelstein2013,Ostlin14} specially at $z\geq2$ since it is when the  line is redshifted into the optical regime.
-LAEs became then a tool to explore the extragalactic Universe and with upcoming telescopes such as the James Webb Space Telescope, new ones are going to be discovered with a better resolution and at higher redshifts.
-This creates then, a clear motivation to model and observe them.
+%1.1 Lyman alpha line
+%1.2 Models
+%1.3 Overview
+
+\subsection{The Lyman Alpha emission line}
+
+The Lyman Alpha ( \lya) emission line is the spectral line produced by an excited hydrogen atom when its electron jumps from the second energy level to the first one.
+This fall causes an emission of a photon with a corresponding wavelenght of $1215.67$ $\AA$.
+The whole Lyman series was discovered in 1906 by the american physicist Theodore Lyman.
 \\
 
-These observations have a direct impact in studying the reionization epoch \cite{review}, properties of the interstellar medium (ISM) and the intergalactic medium (IGM) \citep{Behrens13} \citep{DijkstraKramer}, constraining star formation rates of high redshift galaxies, understanding galaxy luminosity functions \cite{Max} and studying the large scale structure of the Universe.
-In all of these
-studies, an understanding of the processes that model the morphology and the radiate transfer process behind  of the \lya line, is required.
+%(TESIS) se extiende como se descubrió, formula, etc
+
+In 1967 \cite{PartridgePeebles} predicted that young galaxies would have a strong \lya  emission.
+Nowadays galaxies selected using the \lya line are known as Lyman Alpha Emitters (LAEs).
+Since the first observed LAE by \cite{DjorgovskiThompson} different teams have observed several LAEs \citep{Rhoads00,Gawiser2007,Koehler2007,Ouchi08,Yamada2012,Schenker2012,Kulas12, Yamada2012, Chonis2013,Finkelstein2013,Ostlin14,Hayes2014,Faisst2014, Fumagalli2015} specially at $z\geq2$ since it is when the  line is redshifted into the optical regime.
+LAEs became then a tool to explore the extragalactic Universe and with upcoming telescopes such as the James Webb Space Telescope, new ones are going to be discovered with a better resolution and at higher redshifts.
+This creates a clear motivation to model them and observe them.
+\\
+
+As for motivation, these observations have a direct impact in studying the reionization epoch \cite{review}, properties of the interstellar medium (ISM) and the intergalactic medium (IGM) \citep{Behrens13} \citep{DijkstraKramer}, constraining star formation rates of high redshift galaxies, understanding galaxy luminosity functions \cite{Max} and studying the large scale structure of the Universe.
+In all of these studies, an understanding of the processes that model the morphology and radiate transfer process behind the \lya line, is required.
 To fully understand the observed spectra of the LAEs, these galaxies must be modeled.
@@
 
-However the resonant nature of the line makes this a challenging task.
-Analytical solutions for the outcoming spectra in simple ISM static geometries have been derived \cite{Adams72, Harrington73, Neufeld90, Dijkstra06}.
+\subsection{Existing models of Lyman Alpha Emitters}
+
+The resonant nature of the \lya line makes modelling it a challenging task, but constraining the nature of LAEs using the line is a common and strong objective.
+Analytical solutions for the outcoming spectra in simple ISM static geometries have been derived \citep{Adams72, Harrington73, Neufeld90, Dijkstra06}.
 Radiative transfer codes \citep{DijkstraKramer, Laursen09, Verhamme06, CLARA} have been developed in order to understand the effect of the gas kinematics in the \lya line.
 Special attention have been devoted to  the effects of clumpy media \citep{Hansen06} and expanding/contracting shell/spherical geometries started to be studied \citep{Ahn03,Verhamme06,Dijkstra06}.
-Recently, a rotation model, created by Garavito et al.
-\cite{Garavito14} models
-a rotating spherical galaxy with homogeneous gas mixture and analyzes that impact in the \lya line.
 Hydrodynamic simulations have studied the outcomming spectra of LAEs in large scale simulations \cite{Forero12}.
+Escape of \lya photons at the line center is also a proposed model that fits the observations in a more accurate way \citep{Martin2015, Garavito14, Neufeld91}.
 And Monte Carlo codes have been used in hydrodynamic simulations to study in detail individual galaxies \citep{Laursen09,Barnes11,Verhamme12,Yajima12}.\\
 
-Special attention have been devoted to model the presence of outflows in the galaxy, motivated by previous observational studies.
+Special attention have been devoted to model the presence of outflows in these galaxies, motivated by previous observational studies.
 Outflows are a consequence of the interstellar medium (ISM) being ejected from the galaxy due to supernova explosions.
-Here different models have attempt to simulate more realistic situations involving shell models and cavities.
-\citep{Behrens2014}.
-Despite the fact that outflows have been broadly studied, rotation should also be present in this galaxies.
-The joint effect of the above properties should have a direct impact on the morphology of the \lya line.
-This is the subject of this work.
-\\
+Here different models have attempt to simulate more realistic situations involving shell models and cavities \citep{Behrens2014}.
+Blue wings and bumps have been modeled when the outflows regulating the escape of \lya photons are still engulfed within a static interstellar medium \citep{Chung2015}.
+\cite{Verhamme06} created an expanding shell model that despite its geometric simplicity, has been able to fit several \lya profiles including: observational, as the ones studied by \cite{Hashimoto2015} who reproduced the sources \lya lines and calculated their outflow velocities, and simulated, as the ones created by \cite{Gronke2015} who determined if degeneracies exist between the different shell model parameters.
+Also, \cite{Orsi12} creates a wind shell model that could be interpreted as an expanding sphere.
+\cite{Rivera-Thorsen2015} found that no one single effect dominates in governing \lya radiative transfer and escape, and that \lya peak velocities are consistent with a simple model of an intrinsic emission line overlaid by a blueshifted absorption profile from the outﬂowing wind.\\
+
+Despite the fact that outflows have been broadly studied, rotation should also be present in these galaxies.
+Recently, a rotation model, created by Garavito et al.
+\cite{Garavito14} models a rotating spherical galaxy with homogeneous gas mixture and analyzes that impact in the \lya line.
+However not a lot of attention has been payed to this effect in LAEs.\\
+
+The joint effect of the above properties should have a direct impact on the morphology of the \lya line. This is the subject of this work. \\
+
+\subsection{Paper Overview}
 
@@
 
-CAMBIAR ESTOOOOO\\
-
 This paper is structured as follows.
-In \S \ref{sec:theo} we explain in detail the model of rotation and outflow that we use as well and our joint model (Rotation \& Outflow).
-In \S \ref{sec:results} we present the results of our model.
-In \S \ref{sec:discussion} we compare our results with recent observations of LAEs with special attention of those morphologies that present features of galaxy rotation and outflows.
-In the latest section we present our conclusions.
-\\
+In \S \ref{sec:theo} we explain in detail the model of rotation and outflow that we use.
+In \S \ref{sec:results} we present the results of our model, specially how the morphology of the line changes with the free parameters.
+In \S \ref{sec:discussion} we compare our results with a recent observation of a LAE.
+In the latest section \S \ref{sec:conclusions} we present our conclusions and possible future work.
+Finally, in the appendix, we present the results of a \lya modeled only with the rotation analytical soution by \cite{Garavito14} that then is filtered by a \cite{Verhamme06} expanding shell.\\
 
@@
 We approximate that the hydrogen content is $20\%$ the total baryonic content from the cosmological baryon to dark matter  abundances $\Omega_b/\Omega_{dm}=0.1825$ \citep{Planck2015}, multiplied by a primordial Hydrogen fraction of $0.75$.
-All these considerations gives us hydrogen masses in the range $2.7\times 10^{8}-2.7\times 10^{10}$\Msun.\\
+All these considerations gives us hydrogen masses in the range $2.7\times 10^{8}-2.7\times 10^{9}$\Msun.\\
 
 These choices give us a range for the number density of Hydrogen atoms of $4\times10^{-4}-4\times 10^{-3}$ atoms cm$^{-3}$.
-With a Lyman-$\alpha$ cross section at the line center of $\sigma_{H}=1.0\times 10^{-14}$ cm$^{2}$ we finally obtain that the optical depth from the cloud's center  should be in the range $\tau_{\rm H}=2 \times 10^{5} - 2 \times 10^{7}$.
+With a Lyman-$\alpha$ cross section at the line center of $\sigma_{H}=1.0\times 10^{-14}$ cm$^{2}$ we finally obtain that the optical depth from the cloud's center  should be in the range $\tau_{\rm H}=2 \times 10^{5} - 2 \times 10^{6}$.
 \\
@@
 \section{Results}
+\label{sec:results}
 
@@
 
-We acknowledge Alvaro Orsi and Julian Mejia for collaborating with us offering their time, advice and especially data. We used their outflow simulations in order to get our results.\\
+We acknowledge Alvaro Orsi and Julian Mejia for collaborating with us offering their time, advice and especially data. We used their outflow simulations in order to get our results in the appendix.\\
 
